### 2020-01-23 Codebook/MSDS6372.Project.Q2.Rmd
Add files via upload
Question 2 Codebook

---
title: "MSDS 6372 Project"
author: "Jaclyn A Coate"
date: "1/22/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r libraries}
library(tidyverse)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
```

# Question 1:
## Question of Interest: what variables are used to predict price of a NYC Airbnb

```{r data prep}
nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
head(nycraw)
str(nycraw)
```

## EDA to determine type of multiple linear regression to perform

#### Removing logically irrelevant variables

```{r drop irrelevant variables}
#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_reiview", "latitude", "longitude", "neighborhood","availability_365"
nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "minimum_nights", "neighbourhood","availability_365"))
head(nyc2)
```

#### NA Evaluation and Drop

```{r NA eval}
#Checking for NAs
md.pattern(nyc2)
nrow(nyc2)
#Drop NAs that are present
nyc3 <- na.omit(nyc2)
#Confirming NA drop
nrow(nyc3)
```

#### Zero variance variable check - all show variance so remain in model

```{r zero variable check}
#Results show no zero variance variables, leave in all
skim(nyc3)
```

#### Storing all categorical variables as factors

```{r categorical as factors}
#Storing categorical variables as factors
skim(nyc3)
```

#### Checking for Multicollinearity
- Multicollinearity will weaken the model
  - number_of_reviews and reviews_per_month are correlated at 55%
    - Removing reviews_per_month

```{r multicollinearity1}
corrNYC <- nyc3
#Table numeric variables
corrNYCTable <- corrNYC %>% keep(is.numeric) %>% cor %>% view
#Plot numeric variables v numeric variables
corrNYC %>% keep(is.numeric) %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", order="hclust", tl.srt=45, tl.cex = 0.8)
invisible(view(corrNYCTable))
```

```{r attrition: removing highly correlated variable}
#Removing reviews_per_month due to high correlation of is and number_of_reviews
nyc4 <- select(nyc3, -c("reviews_per_month"))
```

#### Summary Review of Data Set

```{r}
summary(nyc4)
```

#### Examining VIFs
- The below results show us there is no need to remove any variables

```{r}
full.model<-lm(price~.,data=nyc4)  # . means all variable not mpg
vif(full.model)[,3]^2

alias(lm(price~.,data=nyc4))
```

## **EDA COMPLETE**

#### Reviewing Linearity with Numeric Variables
- Curved relationships with the numeric variables
  - Could require a quadratic or logarithmic transformation

```{r linearity check}
nyc4 %>% keep(is.numeric) %>% pairs()

par(mfrow=c(2,2))
plot(full.model)
```

```{r drop numeric values}
nyc.final <- nyc4 %>% select(-c("number_of_reviews", "calculated_host_listings_count"))
head(nyc.final)
```

# **** MOVE FORWARD WITH LOG TRANFORAMTIONS / QUADRATIC TRANFORMATIONS TO FIND PREDICTION MODEL WITH NUMERIC VARIABLES FOR QUESTION! ****
#### XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

# Question 2

## 2-Way ANOVA Analysis
- In completing this project with the tools learned in Unit 3 - we will choose to walk away from log transformation and perform a 2-Way ANOVA analysis in order for accuracy as well as simplicity of interpretation of coefficients.

#### Summary Statistics Table
- Creating Mean, SD, SE, Min, Max, and IQR
- Table of graphable statistics

```{r attach data create function sumstats table}
#Attaching the data set
attach(nyc.final)
#Creating a function
nycsummary<-function(x){
  result<-c(length(x),mean(x),sd(x),sd(x)/sqrt(length(x)), min(x), max(x), IQR(x))
  names(result)<-c("N","Mean","SD","SE","Min","Max","IQR")
  return(result)
}
#Creating a summary stats table
nycsumstats<-aggregate(price~neighbourhood_group*room_type,data=nyc.final,nycsummary)
nycsumstats<-cbind(nycsumstats[,1:2],nycsumstats[,-(1:2)])
nycsumstats
```

#### Summary Statistics Graph
- The below graph shows characteristics of a nonadditive model
- Next Steps:
  1. Fit a non-additive model
  2. Check the assumptions
  3. Exmine Type III Sum of Squares F-test tables

```{r sumstats graph}
#means profile plot to visualize the sumstats above
ggplot(nycsumstats,aes(x=neighbourhood_group,y=Mean,group=room_type,colour=room_type))+
  ylab("NYC AirBnBs Prices")+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SD,ymax=Mean+SD),width=.1)

ggplot(nycsumstats,aes(x=room_type,y=Mean,group=neighbourhood_group,colour=neighbourhood_group))+
  ylab("NYC AirBnBs Prices")+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SD,ymax=Mean+SD),width=.1)
```

#### Nonadditive 2-Way ANOVA
- QQ Plot for assumption assessment
  - Show a curve, needs transformation
```{r nonadditive model fit}
#The following code fits the nonadditive two way anova model and then produces the first the main residual diagnostics for assumption checking
nyc.model.fit<-aov(price~neighbourhood_group+room_type+neighbourhood_group:room_type,data=nyc.final)
par(mfrow=c(1,2))
plot(nyc.model.fit$fitted.values,nyc.model.fit$residuals,ylab="Resdiduals",xlab="Fitted")
qqnorm(nyc.model.fit$residuals)
```

#### Log transformation on price

```{r log transformation on price}
#Cannot log zero values, must remove from price variable
nyc.final <- nyc.final[!(nyc.final$price == 0),]
#Auto3 <- Auto[!(Auto$cylinders == 3),]
#Transforming price to logged variable
nyc.log <- nyc.final %>% mutate(lprice=log(price))
view(nyc.log)
```

#### Assumptions check on log transformation of price
- Equal variances: there is some slight variation of variances but this will suffice in order to move forward
- QQ Plot: there is still some slight departure from normality, but again this is acceptable to move forward with our model

```{r assumptions on log price}
nyc.model.fit.log<-aov(lprice~neighbourhood_group+room_type+neighbourhood_group:room_type,data=nyc.log)

par(mfrow=c(1,2))
plot(nyc.model.fit.log$fitted.values,nyc.model.fit.log$residuals,ylab="Resdiduals",xlab="Fitted")
qqnorm(nyc.model.fit.log$residuals)
```

#### Type III F-test table
- From the below F-test table we can see that neighborhood_group, room_type, as well as their interaction are all statistically significant for this model

```{r}
Anova(nyc.model.fit.log,type=3)
```

#### Multiple Test Technique: Tukey-Kramer
- From the F-test table we can see that all current variables are statistically significnat at the 0.05 alpha level
- Move forward with the Tukey-Kramer to discover what factors and/or combinations are contribute to predicting the price of a NYC AirBnB

```{r}
TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95)
plot(TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95))
```

```{r}

```

### 2020-02-05 Codebook/MSDS6372.Project.O1.Rmd
Add files via upload
Newest Object 1 and Object 2 RMD codebooks and accompanying HTML files

---
title: "MSDS 6372 Project 1 Objective 1"
author: "Jaclyn A Coate"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r libraries}
library(tidyverse)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
library(SamplingStrata)
```

# Objective 1:
## Question of Interest: what variables are used to predict price of a NYC Airbnb

```{r data prep}
nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
head(nycraw)
str(nycraw)
```

## EDA to determine type of multiple linear regression to perform

#### Removing logically irrelevant variables

```{r drop irrelevant variables}
#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_reiview", "latitude", "longitude", "neighborhood","availability_365"
nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood","availability_365"))
head(nyc2)
```

#### Dependent Variable Check
- Checking on dependent variable range to make sure if there are zero's to remove. It would not be free to stay in NYC.
```{r}
nyc2 <- nyc2[!(nyc2$price==0),]
invisible(view(nyc2))
```

#### NA Evaluation and Drop

```{r NA eval}
#Checking for NAs
md.pattern(nyc2)
nrow(nyc2)
#Drop NAs that are present
nyc3 <- na.omit(nyc2)
#Confirming NA drop
nrow(nyc3)
```

#### Zero variance variable check - all show variance so remain in model

```{r zero variable check}
#Results show no zero variance variables, leave in all
skim(nyc3)
```

#### Storing all categorical variables as factors

```{r categorical as factors}
#Storing categorical variables as factors
skim(nyc3)
```

#### Checking for Multicollinearity
- Multicollinearity will weaken the model
  - number_of_reviews and reviews_per_month are correlated at 55%
    - Removing reviews_per_month

```{r multicollinearity1}
corrNYC <- nyc3
#Table numeric variables
corrNYCTable <- corrNYC %>% keep(is.numeric) %>% cor %>% view
#Plot numeric variables v numeric variables
corrNYC %>% keep(is.numeric) %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", order="hclust", tl.srt=45, tl.cex = 0.8)
invisible(view(corrNYCTable))
```

```{r attrition: removing highly correlated variable}
#Removing reviews_per_month due to high correlation of is and number_of_reviews
nyc4 <- select(nyc3, -c("reviews_per_month"))
```

#### Summary Review of Data Set

```{r}
summary(nyc4)
```

#### Removing outliers from minimum nights stay
- Anything over 365 is more than a year and would be improbable
- Removing any minimum nights metric over 365

```{r}
nyc4 <- nyc4[!(nyc4$minimum_nights > 365),]
invisible(view(nyc4))
```

#### Examining VIFs
- The below results show us there is no need to remove any variables

```{r}
full.model<-lm(price~.,data=nyc4)  # . means all variable not mpg
vif(full.model)[,3]^2

alias(lm(price~.,data=nyc4))
```

#### Reviewing Linearity with Numeric Variables
- Curved relationships with the numeric variables
  - Could require a quadratic or logarithmic transformation

```{r linearity check}
nyc4 %>% pairs()

par(mfrow=c(2,2))
plot(full.model)
```

#### Creating new Log price variable
- Based on the above plots we may benefit from a transformation
  - Log transforming price to create a log-linear regression

```{r}
log.nyc <- nyc4 %>% mutate(lprice=log(price))
log.nyc <- select(log.nyc, -c("price"))
invisible(log.nyc)
```

#### Examining VIFs of Log Price Variable

```{r}
log.full.model<-lm(lprice~.,data=log.nyc)  # . means all variable not mpg
vif(log.full.model)[,3]^2

alias(lm(lprice~.,data=log.nyc))
```

#### Reviewing Linearity with Independent and Logged Dependent (Price) Variables
- Curved relationships with the numeric variables
  - Could require a quadratic or logarithmic transformation

```{r}
log.nyc  %>% pairs() #[Add color]
#%>% keep(is.numeric)
par(mfrow=c(2,2))
plot(log.full.model)
```

#### Log-log model
- Due to lack of linearity trying to transform the independent variables to see if we can surface a linear relationship
```{r}
log.nyc.independent <- log.nyc %>% mutate(lreviews=log(number_of_reviews))
log.nyc.independent <- log.nyc.independent %>% mutate(lnights=log(minimum_nights))
log.nyc.independent <- log.nyc.independent %>% mutate(llistings=log(calculated_host_listings_count))
invisible(log.nyc.independent)

log.nyc.independent <- select(log.nyc.independent, -c("minimum_nights", "number_of_reviews", "calculated_host_listings_count"))
invisible(log.nyc.independent)
```

#### Examining VIFs of Log-Log Model

```{r}
log.full.model<-lm(lprice~.,data=log.nyc.independent)  # . means all variable not mpg
vif(log.full.model)[,3]^2

alias(lm(lprice~.,data=log.nyc.independent))
```

#### Reviewing Linearity with Logged Independent and Dependent Variables
- Curved relationships with the numeric variables
  - Could require a quadratic or logarithmic transformation

```{r}
log.nyc.independent  %>% pairs() #[Add color]
#%>% keep(is.numeric)

par(mfrow=c(2,2))
plot(log.full.model)
```

#### Continuous Variable Manipulation
- Since we are seeing large clouds of data but no linear trend, we are going to try binning the data to see if it will assist us in determining if there is a relationship between the continuous variables and log price

#```{r}
#data(nyc4)
#nyc4$reviewsBin <- var.bin(nyc4$number_of_reviews, bins = 50)
#nyc4

#nyc4 %>% keep(is.numeric) %>% pairs() #[Add color]

#par(mfrow=c(2,2))
#plot(log.full.model)
#```

### 2020-02-05 Codebook/MSDS6372.Project.O2.Rmd
Add files via upload
Newest Object 1 and Object 2 RMD codebooks and accompanying HTML files

---
title: "MSDS 6372 Project 1 Objective 2"
author: "Jaclyn A Coate"
date: "1/22/2020"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r libraries}
library(tidyverse)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
```

# Objective 1:
## Question of Interest: what variables are used to predict price of a NYC Airbnb

```{r data prep}
nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
head(nycraw)
str(nycraw)
```

## EDA to determine type of multiple linear regression to perform

#### Removing logically irrelevant variables

```{r drop irrelevant variables}
#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_reiview", "latitude", "longitude", "neighborhood","availability_365"
nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood","availability_365"))
head(nyc2)
```

#### Dependent Variable Check
- Checking on dependent variable range to make sure if there are zero's to remove. It would not be free to stay in NYC.
```{r}
nyc2 <- nyc2[!(nyc2$price==0),]
invisible(view(nyc2))
```

#### NA Evaluation and Drop

```{r NA eval}
#Checking for NAs
md.pattern(nyc2)
nrow(nyc2)
#Drop NAs that are present
nyc3 <- na.omit(nyc2)
#Confirming NA drop
nrow(nyc3)
```

#### Zero variance variable check - all show variance so remain in model

```{r zero variable check}
#Results show no zero variance variables, leave in all
skim(nyc3)
```

#### Storing all categorical variables as factors

```{r categorical as factors}
#Storing categorical variables as factors
skim(nyc3)
```

#### Checking for Multicollinearity
- Multicollinearity will weaken the model
  - number_of_reviews and reviews_per_month are correlated at 55%
    - Removing reviews_per_month

```{r multicollinearity1}
corrNYC <- nyc3
#Table numeric variables
corrNYCTable <- corrNYC %>% keep(is.numeric) %>% cor %>% view
#Plot numeric variables v numeric variables
corrNYC %>% keep(is.numeric) %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", order="hclust", tl.srt=45, tl.cex = 0.8)
invisible(view(corrNYCTable))
```

```{r attrition: removing highly correlated variable}
#Removing reviews_per_month due to high correlation of is and number_of_reviews
nyc4 <- select(nyc3, -c("reviews_per_month"))
```

#### Summary Review of Data Set

```{r}
summary(nyc4)
```

#### Removing outliers from minimum nights stay
- Anything over 365 is more than a year and would be improbable
- Removing any minimum nights metric over 365

```{r}
nyc4 <- nyc4[!(nyc4$minimum_nights > 365),]
invisible(view(nyc4))
```

#### Examining VIFs
- The below results show us there is no need to remove any variables

```{r}
full.model<-lm(price~.,data=nyc4)  # . means all variable not mpg
vif(full.model)[,3]^2

alias(lm(price~.,data=nyc4))
```

# Question 2

## 2-Way ANOVA Analysis
- In completing this project with the tools learned in Unit 3 - we will perform a 2-Way ANOVA analysis.

```{r drop numeric values}
nyc.anova <- nyc4 %>% select(-c("number_of_reviews", "calculated_host_listings_count", "minimum_nights"))
head(nyc.anova)
invisible(view(nyc.anova))
```

#### Unbalanced Data
- In reviewing the data we see unbalanced data between the Shared room, Private room, and Entire home/apt indepednet variable levels
- Comapring a shared room leve to a private room or home seems logically irrelevent
- Removing shared room variable
- By removing this leve this model will no longer used for a shared room level of the room_type variable
  - Include this in the conclusion/caveat in scope of inference

```{r}
#Reviewing data levels of room_types
nyc.home <- nyc.anova[(nyc.anova$room_type=="Entire home/apt"),]
nrow(nyc.home)

nyc.private <- nyc.anova[(nyc.anova$room_type=="Private room"),]
nrow(nyc.private)

nyc.shared <- nyc.anova[(nyc.anova$room_type=="Shared room"),]
nrow(nyc.shared)
```

```{r}
#Making final data set with only Private room & Entire home/apt
nyc.anova <- nyc.anova[!(nyc.anova$room_type=="Shared room"),]
invisible(nyc.anova)
```

#### Summary Statistics Table
- Creating Mean, SD, SE, Min, Max, and IQR
- Table of graphable statistics

```{r attach data create function sumstats table}
#Attaching the data set
attach(nyc.anova)
#Creating a function
nycsummary<-function(x){
  result<-c(length(x),mean(x),sd(x),sd(x)/sqrt(length(x)), min(x), max(x), IQR(x))
  names(result)<-c("N","Mean","SD","SE","Min","Max","IQR")
  return(result)
}
#Creating a summary stats table
nycsumstats<-aggregate(price~neighbourhood_group*room_type,data=nyc.anova,nycsummary)
nycsumstats<-cbind(nycsumstats[,1:2],nycsumstats[,-(1:2)])
nycsumstats
```

#### Summary Statistics Graph
#- The below graph shows characteristics of a nonadditive model
#- Next Steps:
#  1. Fit a non-additive model
#  2. Check the assumptions
#  3. Exmine Type III Sum of Squares F-test tables

```{r sumstats graph}
ggplot(nycsumstats,aes(x=room_type,y=Mean,group=neighbourhood_group,colour=neighbourhood_group))+
  ylab("NYC AirBnBs Prices")+xlab("Room Type")+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SD,ymax=Mean+SD),width=.1)
```

#### Nonadditive 2-Way ANOVA
- QQ Plot for assumption assessment
  - Show a curve, needs transformation

```{r nonadditive model fit}
#The following code fits the nonadditive two way anova model and then produces the first the main residual diagnostics for assumption checking
nyc.model.fit<-aov(price~neighbourhood_group+room_type+neighbourhood_group:room_type,data=nyc.anova)

nyc.fits <- data.frame(fitted.values=nyc.model.fit$fitted.values,residuals=nyc.model.fit$residuals)

#Reisudals vs Fitted
nyc.plot1 <- ggplot(nyc.fits, aes(x=fitted.values,y=residuals))+ylab("Residuals")+
  xlab("Predicted")+geom_point()
#QQ Plot of residuals #Note the diagonal abline is only good for qqplots of normal data
nyc.plot2 <- ggplot(nyc.fits,aes(sample=residuals))+
  stat_qq()+geom_abline(intercept=mean(nyc.fits$residuals), slope = sd(nyc.fits$residuals))
#Histograms of residuals
nyc.plot3 <- ggplot(nyc.fits, aes(x=residuals)) + 
  geom_histogram(aes(y=..density..),binwidth=1,color="black", fill="gray")+
  geom_density(alpha=.1, fill="red")
#Grid of all 3 graphs above
grid.arrange(nyc.plot1, nyc.plot2, nyc.plot3, ncol=3)
```

#### Log transformation on price

```{r log transformation on price}
#Cannot log zero values, must remove from price variable
nyc.anova <- nyc.anova[!(nyc.anova$price == 0),]
#Auto3 <- Auto[!(Auto$cylinders == 3),]
#Transforming price to logged variable
nyc.log.anova <- nyc.anova %>% mutate(lprice=log(price))
#view(nyc.final)
```

#### Assumptions check on log transformation of price
- Equal variances: there is some slight variation of variances but this will suffice in order to move forward
- QQ Plot: there is still some slight departure from normality, but again this is acceptable to move forward with our model
- DON'T FORGET TO MENTION CLT - Central Limit Theorum

```{r assumptions on log price}
nyc.model.fit.log<-aov(lprice~neighbourhood_group+room_type+neighbourhood_group:room_type,data=nyc.log.anova)

nyc.fits.log <- data.frame(fitted.values=nyc.model.fit.log$fitted.values,residuals=nyc.model.fit.log$residuals)

#Reisudals vs Fitted
nyc.logplot1 <- ggplot(nyc.fits.log, aes(x=fitted.values,y=residuals))+ylab("Residuals")+
  xlab("Predicted")+geom_point()
#QQ Plot of residuals #Note the diagonal abline is only good for qqplots of normal data
nyc.logplot2 <- ggplot(nyc.fits.log,aes(sample=residuals))+
  stat_qq()+geom_abline(intercept=mean(nyc.fits.log$residuals), slope = sd(nyc.fits.log$residuals))
#Histograms of residuals
nyc.logplot3 <- ggplot(nyc.fits.log, aes(x=residuals)) + 
  geom_histogram(aes(y=..density..),binwidth=1,color="black", fill="gray")+
  geom_density(alpha=.1, fill="red")
#Grid of all 3 graphs above
grid.arrange(nyc.logplot1, nyc.logplot2, nyc.logplot3, ncol=3)
```

#### Outliers
- Since there are not singular points that are aggressively skewing the data, these outliers aren't considered unique or affecting the model in a way that would not be logical.
- Choose to leave all low and high end metrics since the model should take these into account

#### Type III F-test table
- From the below F-test table we can see that neighborhood_group, room_type, as well as their interaction are all statistically significant for this model
- The type-3 sums of squares F-test is provided below. The test for an interaction is not significant (F-stat: 12.493 p-value < .0001). Therefore, we can conclude that the potential changes in AirBnB price for one of the factors does depend on the other.

```{r}
Anova(nyc.model.fit.log,type=3)
```

#### Multiple Test Technique: Tukey-Kramer
- From the F-test table we can see that all current variables are statistically significnat at the 0.05 alpha level
- Move forward with the Tukey-Kramer to discover what factors and/or combinations contribute to predicting the price of a NYC AirBnB

```{r}
nyc.anova.diff <- TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95)
nyc.anova.diff
```

```{r}
plot(TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95))
```

## Multiplicative Effect
- Due to the multiplicative effect caused by interactions the ability to interpret the above model has become challenging.
- In effort to create not only a statistically significant model but a logically relevant model, we are breaking the room_type metric into pieces and comparing them by neighborhood. This allows us to compare apples to apple, due to the fact that comparing the price of a shared room versus an entire home/apt doesn't make sense. The servcies offere are not logically comparible. Therefore breaking out room_type variable and performig three separate 2-way anovas will give us statistically significant data as well as logically applicable data.

### 2020-02-05 Codebook/MSDS6372.Project.O1.Rmd

@@
 library(SamplingStrata)
+library(rbin)
+library(leaps)
 ```
@@
 
-```{r}
+```{r summary of dataset}
 summary(nyc4)
@@
 
-```{r}
+```{r removeing outliers of nights stay}
 nyc4 <- nyc4[!(nyc4$minimum_nights > 365),]
@@
 
-```{r}
+```{r examining VIFs}
 full.model<-lm(price~.,data=nyc4)  # . means all variable not mpg
@@
 ```{r linearity check}
-nyc4 %>% pairs()
+#nyc4 %>% pairs() No color model
+pairs(nyc4,col=nyc4$neighbourhood_group) #Color by neighborhood
 
@@
 
-```{r}
+```{r create logged dependent variable}
 log.nyc <- nyc4 %>% mutate(lprice=log(price))
@@
 
-```{r}
-log.full.model<-lm(lprice~.,data=log.nyc)  # . means all variable not mpg
-vif(log.full.model)[,3]^2
+```{r exmaining log-linear VIFs}
+log.depend.model<-lm(lprice~.,data=log.nyc)  # . means all variable not mpg
+vif(log.depend.model)[,3]^2
 
@@
 
-#### Reviewing Linearity with Independent and Logged Dependent (Price) Variables
+#### Reviewing Linearity with Independent and Logged Dependent (Price) Variable
 - Curved relationships with the numeric variables
@@
 
-```{r}
-log.nyc  %>% pairs() #[Add color]
-#%>% keep(is.numeric)
+```{r linearity check of log-linear model}
+pairs(log.nyc,col=log.nyc$neighbourhood_group)
+
 par(mfrow=c(2,2))
-plot(log.full.model)
+plot(log.depend.model)
 ```
@@
 - Due to lack of linearity trying to transform the independent variables to see if we can surface a linear relationship
-```{r}
-log.nyc.independent <- log.nyc %>% mutate(lreviews=log(number_of_reviews))
-log.nyc.independent <- log.nyc.independent %>% mutate(lnights=log(minimum_nights))
-log.nyc.independent <- log.nyc.independent %>% mutate(llistings=log(calculated_host_listings_count))
-invisible(log.nyc.independent)
+```{r created logged independent variables}
+log.indep.nyc <- log.nyc %>% mutate(lreviews=log(number_of_reviews))
+log.indep.nyc <- log.indep.nyc %>% mutate(lnights=log(minimum_nights))
+log.indep.nyc <- log.indep.nyc %>% mutate(llistings=log(calculated_host_listings_count))
+invisible(log.indep.nyc)
 
-log.nyc.independent <- select(log.nyc.independent, -c("minimum_nights", "number_of_reviews", "calculated_host_listings_count"))
-invisible(log.nyc.independent)
+log.indep.nyc <- select(log.indep.nyc, -c("minimum_nights", "number_of_reviews", "calculated_host_listings_count"))
+invisible(log.indep.nyc)
 ```
@@
 
-```{r}
-log.full.model<-lm(lprice~.,data=log.nyc.independent)  # . means all variable not mpg
-vif(log.full.model)[,3]^2
+```{r examining log-log VIFs}
+log.indep.model<-lm(lprice~.,data=log.indep.nyc)  # . means all variable not mpg
+vif(log.indep.model)[,3]^2
 
-alias(lm(lprice~.,data=log.nyc.independent))
+alias(lm(lprice~.,data=log.indep.nyc))
 ```
@@
 
-```{r}
-log.nyc.independent  %>% pairs() #[Add color]
-#%>% keep(is.numeric)
+```{r linearity check of log-log model}
+pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood_group) #Color by neighborhood
 
 par(mfrow=c(2,2))
-plot(log.full.model)
+plot(log.indep.model)
 ```
@@
 #### Continuous Variable Manipulation
-- Since we are seeing large clouds of data but no linear trend, we are going to try binning the data to see if it will assist us in determining if there is a relationship between the continuous variables and log price
+- Since we are seeing large clouds of data but no linear trend with logged and unlogged data, we are going to move forward with binning the data to see if it will assist us in determining if there is a relationship between the continuous variables and log price
 
-#```{r}
-#data(nyc4)
-#nyc4$reviewsBin <- var.bin(nyc4$number_of_reviews, bins = 50)
-#nyc4
+```{r rbin}
+nyc5 <- rbin_winsorize(nyc4, price, number_of_reviews, 50, winsor_rate = 0.05)
+nyc5
 
-#nyc4 %>% keep(is.numeric) %>% pairs() #[Add color]
+nyc4 %>% keep(is.numeric) %>% pairs() #[Add color]
 
-#par(mfrow=c(2,2))
-#plot(log.full.model)
-#```
+par(mfrow=c(2,2))
+plot(full.model)
+```
+
+#### Continuous Variable Bin Manipulation
+- Since we are seeing large clouds of data but no linear trend with logged and unlogged data, we are going to move forward with binning the data to see if it will assist us in determining if there is a relationship between the continuous variables and log price
+
+```{r var.bin}
+nyc.bins <- nyc4
+
+nyc.bins$reviewsBin <- var.bin(nyc.bins$number_of_reviews, bins = 50)
+nyc.bins$nightsBin <- var.bin(nyc.bins$minimum_nights, bins = 50)
+nyc.bins$listBin <- var.bin(nyc.bins$calculated_host_listings_count, bins = 10)
+
+nyc.bins <- select(nyc.bins,-c("minimum_nights", "number_of_reviews", "calculated_host_listings_count"))
+invisible(nyc.bins)
+```
+
+#### Reviewing Linearity with Binned Indepedent Variables
+- No linearity is presenting itself with a binned approach of the independent variables
+
+```{r linearity check of binned independent variables}
+nyc.bin.model <-lm(price~.,data=nyc.bins)
+#nyc.bins  %>% pairs() No color model
+pairs(nyc.bins,col=nyc.bins$neighbourhood_group) #Color by neighborhood
+
+par(mfrow=c(2,2))
+plot(nyc.bin.model)
+```
+
+#### Explore potential correlation Neighborhood v Price
+- We have to this moment not be able to surface linearity relationships between our numerican independent varaibles and our dependt variable
+- Next we will check for correltaion of the categorical variables: room_type & neighbourhood_group
+- Without removing the ouliers of price above 400 it is near impossible to see if there is a difference per neighborhood. We have removed those prices above 400 to see if the 
+- We see a strong chance of correlation between Price and Neighbourhood Group
+
+```{r}
+nyc.categorical <- nyc4[!(nyc4$price > 400),]
+nrow(nyc4)
+nrow(nyc.categorical)
+plot(nyc.categorical$neighbourhood_group, nyc.categorical$price, xlab = "Neighbourhood Group", ylab = "Price", title = "Price v Neighbourhood Group Correlation Check", col=c(7,32,52,82,107)) 
+```
+
+#### Explore potential correlation Room Type v Price
+- We see a strong chance of corerlation between Price and Room Type
+
+```{r}
+plot(nyc.categorical$room_type, nyc.categorical$price, xlab = "Room Type", ylab = "Price", title = "Price v Room Type Correlation Check", col=c(7,32,52)) 
+```
+
+#### Reviewing Linearity with Numeric Variables w/ Price > 400 Outliers Removed
+
+```{r linearity check w/ Price > 400 Outliers Removed}
+nyc.cat.model<-lm(price~.,data=nyc.categorical) 
+#nyc4 %>% pairs() No color model
+pairs(nyc.categorical,col=nyc.categorical$neighbourhood_group) #Color by neighborhood
+
+par(mfrow=c(2,2))
+plot(nyc.cat.model)
+```
+
+#### Reviewing Linearity with Numeric Variables w/ Log-Linear model Price > 400 Outliers Removed
+- Still no obvious linearity
+
+```{r linearity check w/ Log-Linear model Price > 400 Outliers Removed}
+log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
+
+log.nyc.outliers.model<-lm(lprice~.,data=log.nyc.outliers) 
+pairs(log.nyc.outliers, col=log.nyc.outliers$neighbourhood_group) #Color by neighborhood
+
+par(mfrow=c(2,2))
+plot(log.nyc.outliers.model)
+```
+
+#### Assumptions Check
+- Risduals are normally distributed
+  - Log-linear model has closest to normally distrubuted residuals from last plot
+  - Near normal distriution of residuals
+  - Envoking Central Limit Theorum due to such a large sample size
+- Constant variance
+  - Near normal QQ-plot
+
+```{r residuals, constant variance assumption}
+par(mfrow=c(2,2))
+plot(log.nyc.outliers.model)
+```
+
+- Independence
+  - Assumed
+- Multicollinearity
+  - Confirmed with VIFs and pairs plot that there is no mjultcollinearity occuring
+```{r multicollinearity assumption 2}
+vif(log.depend.model)[,3]^2
+```
+
+```{r multicollinearity assumption}
+pairs(log.nyc.outliers, col=log.nyc.outliers$neighbourhood_group) #Color by neighborhood
+```
+
+- Removed all prices over 400 to help reduce data set and uncover any correlation that was present between the dependent varaibles and independent categorical variables
+```{r outliers assumption}
+#log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
+```
+
+#### Modeling
+- We are not seeing any linear correlation between the dependent and independent numeric varaibles
+- We are seeing a strong chance of linear correlation between the dependent and independent categorical variables
+- We have surfaced the best residuals assumptions matched in a log-linear model
+  - Due to this we are moving forward with modeling a log-linear model with singular variables as well as all interaction terms
+  - This is to add complexity to our model, we have a low number of varaibles to select from
+    - In adding this complexity we are tryign to surface any possible linear variable interations that may contribute to our model
+    - If these are surfaced we will go back and use graphical means to verify the model's discovery
+
+```{r full model check for linearity}
+nyc.model = lm(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers)
+summary(nyc.model)
+```
+
+#### Model selection attempts
+```{r forward selection model}
+nyc.fwd = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="forward",nvmax=20)
+summary(nyc.fwd)$adjr2
+summary(nyc.fwd)$rss
+summary(nyc.fwd)$bic
+```
+
+```{r forward selection model 2}
+nyc.fwd2 = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count, data=log.nyc.outliers, method="forward",nvmax=50)
+summary(nyc.fwd2)$adjr2
+summary(nyc.fwd2)$rss
+summary(nyc.fwd2)$bic
+```
+
+```{r backward selection model}
+nyc.bck = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="backward",nvmax=20)
+summary(nyc.bck)$adjr2
+summary(nyc.bck)$rss
+summary(nyc.bck)$bic
+```
+
+```{r exhaustive selection model}
+nyc.exh = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="exhaustive",nvmax=20)
+summary(nyc.exh)$adjr2
+summary(nyc.exh)$rss
+summary(nyc.exh)$bic
+```
+
+```{r seqrep selection model}
+nyc.seq = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="seqrep",nvmax=20)
+summary(nyc.exh)$adjr2
+summary(nyc.exh)$rss
+summary(nyc.exh)$bic
+```
+
+#### KNN or Random Forest
+- Multiple linear regression is just one option in building a predictive model for a continuous response
+- We are seeing it as a bad option because
+  - The true relationship between the response and predictors is NOT “linear”.  The relationships are complex.
+    - We have gotten close, but we have worked extremely hard in specifying our model and manipulate the raw data to surface a linear relationship
+    - This makes the interpretation into the real world difficult to translate and understand
+  - Since the above is true and our data is very large, we think that other methods such as Random Forest or K-NN would perform better.
+    - These options are less time consuming because the model complexity is built into the lagorithm
+    - We also do not have to specify how a relationship exists ahead of time
+- Since we see a strong relationship between the categorical variables and we have not yet learned Random Forest models, we move forward with a Two-Way ANOVA model to create a sound model to predict the price of a NYC AirBnB.

### 2020-02-05 Codebook/MSDS6372.Project.O2.Rmd

@@
 ```
-
-## Multiplicative Effect
-- Due to the multiplicative effect caused by interactions the ability to interpret the above model has become challenging.
-- In effort to create not only a statistically significant model but a logically relevant model, we are breaking the room_type metric into pieces and comparing them by neighborhood.
-This allows us to compare apples to apple, due to the fact that comparing the price of a shared room versus an entire home/apt doesn't make sense.
-The servcies offere are not logically comparible.
-Therefore breaking out room_type variable and performig three separate 2-way anovas will give us statistically significant data as well as logically applicable data.

### 2020-02-06 Codebook/MSDS6372.Project.O1.Rmd

@@
 ```{r data prep}
-nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
+nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_1/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
 head(nycraw)
@@
 
-```{r linearity check w/ Price > 400 Outliers Removed}
+```{r linearity check w Price greater than 400 Outliers Removed}
 nyc.cat.model<-lm(price~.,data=nyc.categorical) 
@@
 
-```{r linearity check w/ Log-Linear model Price > 400 Outliers Removed}
+```{r linearity check w Log-Linear model Price greater than 400 Outliers Removed}
 log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
@@
 plot(log.nyc.outliers.model)
-```
-
-#### Assumptions Check
-- Risduals are normally distributed
-  - Log-linear model has closest to normally distrubuted residuals from last plot
-  - Near normal distriution of residuals
-  - Envoking Central Limit Theorum due to such a large sample size
-- Constant variance
-  - Near normal QQ-plot
-
-```{r residuals, constant variance assumption}
-par(mfrow=c(2,2))
-plot(log.nyc.outliers.model)
-```
-
-- Independence
-  - Assumed
-- Multicollinearity
-  - Confirmed with VIFs and pairs plot that there is no mjultcollinearity occuring
-```{r multicollinearity assumption 2}
-vif(log.depend.model)[,3]^2
-```
-
-```{r multicollinearity assumption}
-pairs(log.nyc.outliers, col=log.nyc.outliers$neighbourhood_group) #Color by neighborhood
-```
-
-- Removed all prices over 400 to help reduce data set and uncover any correlation that was present between the dependent varaibles and independent categorical variables
-```{r outliers assumption}
-#log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
 ```
@@
 
-```{r full model check for linearity}
+```{r full model check for p-value significance}
 nyc.model = lm(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers)
@@
 
-#### KNN or Random Forest
+#### Assumptions Check
+- Risduals are normally distributed
+  - Log-linear model has closest to normally distrubuted residuals from last plot
+  - Near normal distriution of residuals
+  - Envoking Central Limit Theorum due to such a large sample size
+- Constant variance
+  - Near normal QQ-plot
+
+```{r residuals, constant variance assumption}
+par(mfrow=c(2,2))
+plot(log.nyc.outliers.model)
+```
+
+- Independence
+  - Assumed
+- Multicollinearity
+  - Confirmed with VIFs and pairs plot that there is no mjultcollinearity occuring
+
+```{r multicollinearity assumption two}
+vif(log.depend.model)[,3]^2
+```
+
+```{r multicollinearity assumption}
+pairs(log.nyc.outliers, col=log.nyc.outliers$neighbourhood_group) #Color by neighborhood
+```
+
+- Removed all prices over 400 to help reduce data set and uncover any correlation that was present between the dependent varaibles and independent categorical variables
+
+```{r outliers assumption}
+#log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
+```
+
+#### MLR May Not Be The Best
 - Multiple linear regression is just one option in building a predictive model for a continuous response
@@
   - The true relationship between the response and predictors is NOT “linear”.  The relationships are complex.
-    - We have gotten close, but we have worked extremely hard in specifying our model and manipulate the raw data to surface a linear relationship
-    - This makes the interpretation into the real world difficult to translate and understand
+    - We have gotten close, but we have worked extremely hard in specifying our model and manipulating the raw data to surface a linear relationship
+    - This makes the interpretation into the real world application difficult to interpret
   - Since the above is true and our data is very large, we think that other methods such as Random Forest or K-NN would perform better.
@@
     - We also do not have to specify how a relationship exists ahead of time
-- Since we see a strong relationship between the categorical variables and we have not yet learned Random Forest models, we move forward with a Two-Way ANOVA model to create a sound model to predict the price of a NYC AirBnB.
+- Since we see a strong relationship between the categorical variables, we move forward with a Two-Way ANOVA model to create a model way predict the price of a NYC AirBnB.

### 2020-02-07 Codebook/MSDS6372.Project.O1.Rmd

@@
 - Due to lack of linearity trying to transform the independent variables to see if we can surface a linear relationship
+
 ```{r created logged independent variables}
@@
 #### Model selection attempts
+
 ```{r forward selection model}

### 2020-02-08 Project1_RM.Rmd
Add files via upload

---
title: "Project1_RM"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(geosphere)

options(scipen=999)
```

```{r}
knitr::opts_chunk$set(echo = TRUE)
airbnb <-read.csv(file="/Users/reagan/Documents/_SMU/Spring_2020/Applied_Statistics/Applied_Stats_Project/Project_1/AB_NYC_2019.csv",header=TRUE)

airbnb <- filter(airbnb, substr(last_review, 1, 4) %in% c('2017', '2018', '2019'))

airbnb <- filter(airbnb, price >= 25 & price <= 400)

airbnb$id <- NULL
airbnb$name <- NULL
airbnb$host_id <- NULL
airbnb$host_name <- NULL
airbnb$host_listings <- airbnb$calculated_host_listings
airbnb$calculated_host_listings <- NULL

#Creating a new, tsquare_distance (distance to Times Square in miles)
for (i in 1:nrow(airbnb)) {
  n <- (distHaversine(c(airbnb$latitude[i], -airbnb$longitude[i]), c(40.7580, 73.9855)) / 1609.344)
  airbnb$tsquare_distance[i] <- n
}

selected_vars <- c('neighbourhood_group', 'neighbourhood', 'room_type', 'price', 'minimum_nights', 'number_of_reviews', 'reviews_per_month', 'host_listings', 'tsquare_distance', 'availability_365')
airbnb <- airbnb[selected_vars]

airbnb <- airbnb[!(airbnb$price==0),]
airbnb <- airbnb[!(airbnb$availability_365==0),]

airbnb_EH <- filter(airbnb, room_type == "Entire home/apt")
airbnb_PR <- filter(airbnb, room_type == "Private room")
airbnb_SR <- filter(airbnb, room_type == "Shared room")
```

```{r}
fit <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = airbnb)
summary(fit)
plot(fit)
```

### 2020-02-09 Codebook/MSDS6372.Project.O1.Rmd

@@
 library(leaps)
+library(dplyr)
+library(ggplot2)
+library(geosphere)
+library(broom)
+library(plyr)
+library(devtools)
+options(scipen=999)
 ```
@@
 
+#### Determined that Times Square is a hot destination point. Used Lat long metrics to build a new metric with distance to Times Square
+
+```{r tsquare_distance metric}
+#Creating a new, tsquare_distance (distance to Times Square in miles)
+for (i in 1:nrow(nycraw)) {
+  n <- (distHaversine(c(nycraw$latitude[i], -nycraw$longitude[i]), c(40.7580, 73.9855)) / 1609.344)
+  nycraw$tsquare_distance[i] <- n
+}
+head(nycraw)
+```
+
 #### Removing logically irrelevant variables
@@
 ```{r drop irrelevant variables}
-#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_reiview", "latitude", "longitude", "neighborhood","availability_365"
-nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood","availability_365"))
+#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighborhood"
+nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood_group"))
 head(nyc2)
@@
 
-#### Dependent Variable Check
+#### Zero Value Variable Check
 - Checking on dependent variable range to make sure if there are zero's to remove. It would not be free to stay in NYC.
-```{r}
+- Checking on independent variables that have '0' as a value. Seeing that "availability_365" would mean the AirBnB isn't available at all, we are dropping those from our data set.
+```{r zero value variable check}
 nyc2 <- nyc2[!(nyc2$price==0),]
+nyc2 <- nyc2[!(nyc2$availability_365==0),]
 invisible(view(nyc2))
@@
 
-```{r zero variable check}
+#```{r zero variable check}
 #Results show no zero variance variables, leave in all
-skim(nyc3)
-```
+#skim(nyc3)
+#```
 
@@
 
-#### Checking for Multicollinearity
+### Numerical v Numerical Multicollinearity
 - Multicollinearity will weaken the model
@@
 
+#### Changing Price variable range
+```{r}
+nyc4 <- filter(nyc4, price >= 25 & price <= 400)
+```
+
 #### Removing outliers from minimum nights stay
@@
 
-#### Examining VIFs
-- The below results show us there is no need to remove any variables
-
-```{r examining VIFs}
-full.model<-lm(price~.,data=nyc4)  # . means all variable not mpg
-vif(full.model)[,3]^2
-
-alias(lm(price~.,data=nyc4))
-```
-
 #### Reviewing Linearity with Numeric Variables
@@
 #nyc4 %>% pairs() No color model
-pairs(nyc4,col=nyc4$neighbourhood_group) #Color by neighborhood
-
-par(mfrow=c(2,2))
-plot(full.model)
+pairs(nyc4,col=nyc4$neighbourhood) #Color by neighborhood
 ```
@@
 
-#### Examining VIFs of Log Price Variable
-
-```{r exmaining log-linear VIFs}
-log.depend.model<-lm(lprice~.,data=log.nyc)  # . means all variable not mpg
-vif(log.depend.model)[,3]^2
-
-alias(lm(lprice~.,data=log.nyc))
-```
-
-#### Reviewing Linearity with Independent and Logged Dependent (Price) Variable
+#### Reviewing Linearity with Log-Linear model: Independent and Logged Dependent (Price) Variable
 - Curved relationships with the numeric variables
@@
 ```{r linearity check of log-linear model}
-pairs(log.nyc,col=log.nyc$neighbourhood_group)
-
-par(mfrow=c(2,2))
-plot(log.depend.model)
+pairs(log.nyc,col=log.nyc$neighbourhood)
 ```
@@
 log.indep.nyc <- log.indep.nyc %>% mutate(llistings=log(calculated_host_listings_count))
+log.indep.nyc <- log.indep.nyc %>% mutate(lavailablility=log(availability_365))
+log.indep.nyc <- log.indep.nyc %>% mutate(ltsqr=log(tsquare_distance))
 invisible(log.indep.nyc)
 
-log.indep.nyc <- select(log.indep.nyc, -c("minimum_nights", "number_of_reviews", "calculated_host_listings_count"))
+log.indep.nyc <- select(log.indep.nyc, -c("minimum_nights", "number_of_reviews", "calculated_host_listings_count", "availability_365", "tsquare_distance"))
+# Checking for -inf logged results
 invisible(log.indep.nyc)
-```
-
-#### Examining VIFs of Log-Log Model
-
-```{r examining log-log VIFs}
-log.indep.model<-lm(lprice~.,data=log.indep.nyc)  # . means all variable not mpg
-vif(log.indep.model)[,3]^2
-
-alias(lm(lprice~.,data=log.indep.nyc))
+# Drop -inf log reults in lavailability
+log.indep.nyc<-log.indep.nyc[!(log.indep.nyc$lavailablility=="-Inf"),]
+invisible(log.indep.nyc)
 ```
@@
 ```{r linearity check of log-log model}
-pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood_group) #Color by neighborhood
-
-par(mfrow=c(2,2))
-plot(log.indep.model)
-```
-
-#### Continuous Variable Manipulation
-- Since we are seeing large clouds of data but no linear trend with logged and unlogged data, we are going to move forward with binning the data to see if it will assist us in determining if there is a relationship between the continuous variables and log price
-
-```{r rbin}
-nyc5 <- rbin_winsorize(nyc4, price, number_of_reviews, 50, winsor_rate = 0.05)
-nyc5
-
-nyc4 %>% keep(is.numeric) %>% pairs() #[Add color]
-
-par(mfrow=c(2,2))
-plot(full.model)
+pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood) #Color by neighborhood
 ```
@@
 nyc.bins$nightsBin <- var.bin(nyc.bins$minimum_nights, bins = 50)
+nyc.bins$availBin <- var.bin(nyc.bins$availability_365, bins = 50)
 nyc.bins$listBin <- var.bin(nyc.bins$calculated_host_listings_count, bins = 10)
 
-nyc.bins <- select(nyc.bins,-c("minimum_nights", "number_of_reviews", "calculated_host_listings_count"))
+nyc.bins <- select(nyc.bins,-c("minimum_nights", "number_of_reviews", "calculated_host_listings_count", "availability_365"))
 invisible(nyc.bins)
@@
 #nyc.bins  %>% pairs() No color model
-pairs(nyc.bins,col=nyc.bins$neighbourhood_group) #Color by neighborhood
-
-par(mfrow=c(2,2))
-plot(nyc.bin.model)
+pairs(nyc.bins,col=nyc.bins$neighbourhood) #Color by neighborhood
 ```
@@
 #### Explore potential correlation Neighborhood v Price
-- We have to this moment not be able to surface linearity relationships between our numerican independent varaibles and our dependt variable
+- We have to this moment not be able to surface linearity relationships between our numerican independent varaibles and our dependentt variable
 - Next we will check for correltaion of the categorical variables: room_type & neighbourhood_group
-- Without removing the ouliers of price above 400 it is near impossible to see if there is a difference per neighborhood. We have removed those prices above 400 to see if the 
 - We see a strong chance of correlation between Price and Neighbourhood Group
@@
 ```{r}
-nyc.categorical <- nyc4[!(nyc4$price > 400),]
-nrow(nyc4)
-nrow(nyc.categorical)
-plot(nyc.categorical$neighbourhood_group, nyc.categorical$price, xlab = "Neighbourhood Group", ylab = "Price", title = "Price v Neighbourhood Group Correlation Check", col=c(7,32,52,82,107)) 
+plot(nyc4$neighbourhood, nyc4$price, xlab = "Neighbourhood", ylab = "Price", title = "Price v Neighbourhood Correlation Check", col=c(7,32,52,82,107)) 
+```
+
+- Narrowing down neighborhoods (randomly) to confirm neighbourhood is a significant categorical metrics to keep in MLR
+
+```{r}
+nycNeighborhood <- ddply(nyc4,.(neighbourhood), function(x) x[sample(nrow(x),1),])
+
+plot(nycNeighborhood$neighbourhood, nycNeighborhood$price, xlab = "Neighbourhood", ylab = "Price", title = "Price v Neighbourhood Correlation Check") 
 ```
@@
 ```{r}
-plot(nyc.categorical$room_type, nyc.categorical$price, xlab = "Room Type", ylab = "Price", title = "Price v Room Type Correlation Check", col=c(7,32,52)) 
-```
-
-#### Reviewing Linearity with Numeric Variables w/ Price > 400 Outliers Removed
-
-```{r linearity check w Price greater than 400 Outliers Removed}
-nyc.cat.model<-lm(price~.,data=nyc.categorical) 
-#nyc4 %>% pairs() No color model
-pairs(nyc.categorical,col=nyc.categorical$neighbourhood_group) #Color by neighborhood
-
-par(mfrow=c(2,2))
-plot(nyc.cat.model)
-```
-
-#### Reviewing Linearity with Numeric Variables w/ Log-Linear model Price > 400 Outliers Removed
-- Still no obvious linearity
-
-```{r linearity check w Log-Linear model Price greater than 400 Outliers Removed}
-log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
-
-log.nyc.outliers.model<-lm(lprice~.,data=log.nyc.outliers) 
-pairs(log.nyc.outliers, col=log.nyc.outliers$neighbourhood_group) #Color by neighborhood
-
-par(mfrow=c(2,2))
-plot(log.nyc.outliers.model)
+plot(nyc4$room_type, nyc4$price, xlab = "Room Type", ylab = "Price", title = "Price v Room Type Correlation Check", col=c(7,32,52)) 
 ```
@@
 - We are not seeing any linear correlation between the dependent and independent numeric varaibles
-- We are seeing a strong chance of linear correlation between the dependent and independent categorical variables
+  - We have tried: linear regression, log-linear regression transformation, log-log regression transformation, binning, and outlier drop.
+- We are seeing a strong linear correlation between the dependent and independent categorical variables
 - We have surfaced the best residuals assumptions matched in a log-linear model
@@
 
-```{r full model check for p-value significance}
-nyc.model = lm(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers)
+```{r full model check}
+nyc.model = lm(lprice~neighbourhood + room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + tsquare_distance, data=log.nyc)
 summary(nyc.model)
+
+#Surfacing only significant neighborhoods
+nyc.model2 = tidy(nyc.model)
+options(scipen = 999)
+invisible(nyc.model2)
+nyc.modeldf <- nyc.model2[nyc.model2$p.value < 0.05,]
+invisible(view(nyc.modeldf))
+```
+
+```{r}
+#would reducing the data set to just sig values help?
 ```
@@
 
-```{r forward selection model}
-nyc.fwd = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="forward",nvmax=20)
-summary(nyc.fwd)$adjr2
-summary(nyc.fwd)$rss
-summary(nyc.fwd)$bic
+```{r intuitive model}
+#To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared
 ```
 
-```{r forward selection model 2}
-nyc.fwd2 = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count, data=log.nyc.outliers, method="forward",nvmax=50)
-summary(nyc.fwd2)$adjr2
-summary(nyc.fwd2)$rss
-summary(nyc.fwd2)$bic
+```{r forward selection model}
+nyc.fwd = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method = "forward", data=log.nyc, nvmax=20)
+summary(nyc.fwd)$adjr2
+
+#predict.regsubsets =function (object , newdata ,id ,...){
+#  form=as.formula (object$call [[2]])
+#  mat=model.matrix(form ,newdata )
+#  coefi=coef(object ,id=id)
+#  xvars=names(coefi)
+#  mat[,xvars]%*%coefi
+#}
+
+#testASE<-c()
+#note my index is to 20 since that what I set it in regsubsets
+#for (i in 1:20){
+#  predictions<-predict.regsubsets(object=reg.fwd,newdata=test,id=i) 
+#  testASE[i]<-mean((log(test$AvgWinnings)-predictions)^2)
+#}
+
+#par(mfrow=c(1,1))
+#plot(1:20,testASE,type="l",xlab="# of predictors",ylab="test vs train ASE",ylim=c(0.2,0.8))
+
+#index<-which(testASE==min(testASE))
+#points(index,testASE[index],col="red",pch=10)
+#rss<-summary(reg.fwd)$rss
+#lines(1:20,rss/100,lty=3,col="blue")  #Dividing by 100 since ASE=RSS/sample size
+
+#coef(reg.final,XXXX)
+
+#final.model<-lm(log(AvgWinnings)~Greens+AvgPutts+Save,data=golf)
+#summary(final.model)
 ```
@@
 ```{r backward selection model}
-nyc.bck = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="backward",nvmax=20)
+nyc.bck = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="backward", data=log.nyc, nvmax=20)
 summary(nyc.bck)$adjr2
-summary(nyc.bck)$rss
-summary(nyc.bck)$bic
+#summary(nyc.bck)$rss
+#summary(nyc.bck)$bic
+```
+
+```{r seqrep selection model}
+nyc.seq = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="seqrep", data=log.nyc, nvmax=20)
+summary(nyc.seq)$adjr2
+#summary(nyc.seq)$rss
+#summary(nyc.seq)$bic
 ```
@@
 ```{r exhaustive selection model}
-nyc.exh = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="exhaustive",nvmax=20)
-summary(nyc.exh)$adjr2
-summary(nyc.exh)$rss
-summary(nyc.exh)$bic
+#Due to an exhaustive method being too large. We are commenting out this model and moving forward with selective methods that will run
+#nyc.exh = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, data=log.nyc, nvmax=20)
+#summary(nyc.exh)$adjr2
+#summary(nyc.exh)$rss
+#summary(nyc.exh)$bic
 ```
 
-```{r seqrep selection model}
-nyc.seq = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="seqrep",nvmax=20)
-summary(nyc.exh)$adjr2
-summary(nyc.exh)$rss
-summary(nyc.exh)$bic
+#### Assumptions Check on Intuitive Model
+- Residuals near normally distributed but still skewed
+- Envoking Central Limit Theorum due to such a large sample size
+- Constant Variance
+  - The QQ Plot shows an extreme deviation from normality. Even with the Central Limit Theorum we do not feel comforablte moving forward.
+
+```{r Assumptions Check on Intuitive Model}
+par(mfrow=c(2,2))
+full.model<-lm(price~.,data=nyc4)
+plot(full.model)
 ```
 
-#### Assumptions Check
-- Risduals are normally distributed
-  - Log-linear model has closest to normally distrubuted residuals from last plot
-  - Near normal distriution of residuals
+#### Assumptions Check on Log-Linear Intuitive Model
+- Risduals are near normally distributed with them being slightly off
   - Envoking Central Limit Theorum due to such a large sample size
+  - Passed
 - Constant variance
-  - Near normal QQ-plot
+  - The QQ-plot is showing much less departure from normality
+  - Passed
 
-```{r residuals, constant variance assumption}
+```{r Assumptions Check on Log-Linear Intuitive Model}
 par(mfrow=c(2,2))
-plot(log.nyc.outliers.model)
+log.depend.model<-lm(lprice~.,data=log.nyc)
+plot(log.depend.model)
 ```
@@
   - Assumed
+  - Passed
 - Multicollinearity
-  - Confirmed with VIFs and pairs plot that there is no mjultcollinearity occuring
+  - We are seeing a high VIF for our distance to Times Square
 
-```{r multicollinearity assumption two}
+```{r Multicollinearity Assumption on Log-Linear Intuitive Model}
 vif(log.depend.model)[,3]^2
-```
-
-```{r multicollinearity assumption}
-pairs(log.nyc.outliers, col=log.nyc.outliers$neighbourhood_group) #Color by neighborhood
-```
-
-- Removed all prices over 400 to help reduce data set and uncover any correlation that was present between the dependent varaibles and independent categorical variables
-
-```{r outliers assumption}
-#log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
 ```

### 2020-02-11 Project1_RM.Rmd
Update Project1_RM.Rmd

@@
 
+Loading libraries and settings
 ```{r setup, include=FALSE}
@@
 library(geosphere)
-
 options(scipen=999)
+options(max.print=1000000)
 ```
 
+Exploratory Data Analysis
 ```{r}
 knitr::opts_chunk$set(echo = TRUE)
-airbnb <-read.csv(file="/Users/reagan/Documents/_SMU/Spring_2020/Applied_Statistics/Applied_Stats_Project/Project_1/AB_NYC_2019.csv",header=TRUE)
+#MAC
+#airbnb <- read.csv(file="/Users/reagan/Documents/_SMU/Spring_2020/Applied_Statistics/Applied_Stats_Project/Project_1/AB_NYC_2019.csv",header=TRUE)
+
+#PC
+airbnb <- read.csv(file="C:/Users/EREAMEA/Documents/_SMU/Applied Statistics/Semester Project/AB_NYC_2019.csv",header=TRUE)
 
@@
 
+Full data set regression fit with interaction term, no transformation
 ```{r}
-fit <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = airbnb)
+fit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = airbnb)
 summary(fit)
@@
 ```
+
+Full data set regression fit with interaction term, log - linear transformation
+```{r}
+fit_log <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = airbnb)
+summary(fit_log)
+plot(fit_log)
+```
+
+Entire home/apt data set regression fit, log - linear transformation
+```{r}
+fit_EH <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood, data = airbnb_EH)
+summary(fit_EH)
+plot(fit_EH)
+```
+
+Private room data set regression fit, log - linear transformation
+```{r}
+fit_PR <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood, data = airbnb_EH)
+summary(fit_EH)
+plot(fit_PR)
+```
+
+Shared room data set regression fit, log - linear transformation
+```{r}
+fit_SR <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood, data = airbnb_EH)
+summary(fit_SR)
+plot(fit_SR)
+```

### 2020-02-11 WorkingCode/Objective1.Work.Rmd
Add files via upload
Working code

---
title: "xxx"
author: "Jaclyn A Coate"
date: "2/9/2020"
output: html_document
---

#### Checking for Multicollinearity
### Numerical v Numerical Multicollinearity
- Multicollinearity will weaken the model
  - number_of_reviews and reviews_per_month are correlated at 55%
    - Removing reviews_per_month

```{r multicollinearity1}
corrNYC <- nyc3
#Table numeric variables
corrNYCTable <- corrNYC %>% keep(is.numeric) %>% cor %>% view
#Plot numeric variables v numeric variables
corrNYC %>% keep(is.numeric) %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", order="hclust", tl.srt=45, tl.cex = 0.8)
invisible(view(corrNYCTable))
```

```{r attrition: removing highly correlated variable}
#Removing reviews_per_month due to high correlation of is and number_of_reviews
nyc4 <- select(nyc3, -c("reviews_per_month"))
```

### Examining VIFs for Multicollinearity of No Transformation
- The below results show us there is no need to remove any variables

```{r examining VIFs}
full.model<-lm(price~.,data=nyc4)  # . means all variable not mpg
vif(full.model)[,3]^2

alias(lm(price~.,data=nyc4))
```

#### Assumptions of Model

```{r}
par(mfrow=c(2,2))
full.model<-lm(price~.,data=nyc4)
plot(full.model)
```

#### Examining VIFs of Log Price Variable

```{r exmaining log-linear VIFs}
log.depend.model<-lm(lprice~.,data=log.nyc)  # . means all variable not mpg
vif(log.depend.model)[,3]^2

alias(lm(lprice~.,data=log.nyc))
```

#### Assumptions of Log-Linear Model

```{r}
par(mfrow=c(2,2))
log.depend.model<-lm(lprice~.,data=log.nyc)
plot(log.depend.model)
```

#### Examining VIFs of Log-Log Model

```{r examining log-log VIFs}
log.indep.model<-lm(lprice~.,data=log.indep.nyc)  # . means all variable not mpg
vif(log.indep.model)[,3]^2

alias(lm(lprice~.,data=log.indep.nyc))
```

#### Assumptions of Log-Log Model

```{r}
par(mfrow=c(2,2))
log.indep.model<-lm(lprice~.,data=log.indep.nyc)
plot(log.indep.model)
```

#### Assumptions of Binned Data

```{r}
par(mfrow=c(2,2))
plot(nyc.bin.model)
```

### 2020-02-11 Codebook/MSDS6372.Project.O1.Rmd
Update MSDS6372.Project.O1.Rmd

@@
 #To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared
+
+rfit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
+summary(rfit)
+plot(rfit)
+
+rfitl <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
+summary(rfitl)
+plot(rfitl)
+
 ```

### 2020-02-11 Codebook/MSDS6372.Project.O1.Rmd
Update MSDS6372.Project.O1.Rmd

@@
 
-rfitl <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
+rfitl <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc4)
 summary(rfitl)
 plot(rfitl)
-
 ```

### 2020-02-11 Codebooks/MSDS6372.Project.O1.Rmd

--- 2020-02-09 Codebook/MSDS6372.Project.O1.Rmd
@@
 library(devtools)
+library(leaps)
 options(scipen=999)
@@
 nyc.bins$listBin <- var.bin(nyc.bins$calculated_host_listings_count, bins = 10)
+nyc.bins$tsquBin <- var.bin(nyc.bins$tsquare_distance, bins = 20)
 
-nyc.bins <- select(nyc.bins,-c("minimum_nights", "number_of_reviews", "calculated_host_listings_count", "availability_365"))
+nyc.bins <- select(nyc.bins,-c("minimum_nights", "number_of_reviews", "calculated_host_listings_count", "availability_365", "tsquare_distance"))
 invisible(nyc.bins)
@@
 #To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared
+rfit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
+summary(rfit)
+plot(rfit)
+rfitl <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc4)
+summary(rfitl)
+plot(rfitl)
 ```
@@
 
-#predict.regsubsets =function (object , newdata ,id ,...){
-#  form=as.formula (object$call [[2]])
-#  mat=model.matrix(form ,newdata )
-#  coefi=coef(object ,id=id)
-#  xvars=names(coefi)
-#  mat[,xvars]%*%coefi
-#}
+fwd.adjr2 <- summary(nyc.fwd)$adjr2
+plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
+fwd.index <- which(adjr2 == max(adjr2))
+points(fwd.index, adjr2[fwd.index],col="red", pch=10)
+```
 
-#testASE<-c()
-#note my index is to 20 since that what I set it in regsubsets
-#for (i in 1:20){
-#  predictions<-predict.regsubsets(object=reg.fwd,newdata=test,id=i) 
-#  testASE[i]<-mean((log(test$AvgWinnings)-predictions)^2)
-#}
+- Below are the final coeffecients based on the above forwad selection model with highest Adjusted r-squared at 15
 
-#par(mfrow=c(1,1))
-#plot(1:20,testASE,type="l",xlab="# of predictors",ylab="test vs train ASE",ylim=c(0.2,0.8))
-
-#index<-which(testASE==min(testASE))
-#points(index,testASE[index],col="red",pch=10)
-#rss<-summary(reg.fwd)$rss
-#lines(1:20,rss/100,lty=3,col="blue")  #Dividing by 100 since ASE=RSS/sample size
-
-#coef(reg.final,XXXX)
-
-#final.model<-lm(log(AvgWinnings)~Greens+AvgPutts+Save,data=golf)
-#summary(final.model)
+```{r}
+coef(nyc.fwd,15)
 ```
@@
 summary(nyc.bck)$adjr2
-#summary(nyc.bck)$rss
-#summary(nyc.bck)$bic
+
+bck.adjr2 <- summary(nyc.bck)$adjr2
+plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
+bck.index <- which(adjr2 == max(adjr2))
+points(bck.index, adjr2[bck.index],col="red", pch=10)
+```
+
+- Below are the final coeffecients based on the above backward selection model with highest Adjusted r-squared at 15
+
+```{r}
+coef(nyc.bck,15)
 ```
@@
 summary(nyc.seq)$adjr2
-#summary(nyc.seq)$rss
-#summary(nyc.seq)$bic
+
+bck.adjr2 <- summary(nyc.bck)$adjr2
+plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
+bck.index <- which(adjr2 == max(adjr2))
+points(bck.index, adjr2[bck.index],col="red", pch=10)
 ```
@@
 
+### XXXXXXXX
+
 ```{r Assumptions Check on Intuitive Model}
@@
 full.model<-lm(price~.,data=nyc4)
-plot(full.model)
+plot(XXXXXXX)
 ```
@@
   - Passed
+
+### XXXXXXXXX
 

### 2020-02-11 Codebooks/MSDS6372.Project.O2.Rmd

--- 2020-02-11 Codebooks/MSDS6372.Project.O1.Rmd
@@
 ---
-title: "MSDS 6372 Project 1 Objective 1"
+title: "MSDS 6372 Project 1 Objective 2"
 author: "Jaclyn A Coate"
-date: "2/5/2020"
-output: html_document
+date: "1/22/2020"
+output:
+  html_document: default
+  word_document: default
 ---
@@
 library(devtools)
-library(leaps)
 options(scipen=999)
@@
 
-# Objective 1:
-## Question of Interest: what variables are used to predict price of a NYC Airbnb
+# Objective 2 EDA:
 
 ```{r data prep}
-nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_1/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
+nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
 head(nycraw)
 str(nycraw)
+nrow(nycraw)
 ```
@@
 ```
-
-#### Zero variance variable check - all show variance so remain in model
-
-#```{r zero variable check}
-#Results show no zero variance variables, leave in all
-#skim(nyc3)
-#```
 
@@
 - We have surfaced the best residuals assumptions matched in a log-linear model
-  - Due to this we are moving forward with modeling a log-linear model with singular variables as well as all interaction terms
-  - This is to add complexity to our model, we have a low number of varaibles to select from
-    - In adding this complexity we are tryign to surface any possible linear variable interations that may contribute to our model
-    - If these are surfaced we will go back and use graphical means to verify the model's discovery
+  - Due to these discoveries we are moving forward with a Two-Way ANOVA in order to create the strongest model
+- The number of Neighborhoods is so high deriving any sort of practical significance in a two-way ANOVA would be too difficult. 
+  - Changing our selected variables to Neighbourhod_Group and room_type
 
-```{r full model check}
-nyc.model = lm(lprice~neighbourhood + room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + tsquare_distance, data=log.nyc)
-summary(nyc.model)
+#### Clean data for Two-Way ANOVA
 
-#Surfacing only significant neighborhoods
-nyc.model2 = tidy(nyc.model)
-options(scipen = 999)
-invisible(nyc.model2)
-nyc.modeldf <- nyc.model2[nyc.model2$p.value < 0.05,]
-invisible(view(nyc.modeldf))
+```{r data prep2}
+nyc.anova.raw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
+head(nyc.anova.raw)
+nyc.anova.raw2 <- select(nyc.anova.raw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood", "minimum_nights", "number_of_reviews", "last_review", "reviews_per_month", "calculated_host_listings_count", "availability_365"))
+head(nyc.anova.raw2)
+
+nyc.anova.raw2 <- filter(nyc.anova.raw2, price >= 25 & price <= 400)
+invisible(view(nyc.anova.raw2))
 ```
 
-```{r}
-#would reducing the data set to just sig values help?
+## Start 2-Way ANOVA Analysis
+- In completing this project with the tools learned in Unit 3 - we will perform a 2-Way ANOVA analysis.
+
+#### Summary Statistics Table
+- Creating Mean, SD, SE, Min, Max, and IQR
+- Table of graphable statistics
+
+```{r attach data create function sumstats table}
+nyc.anova <- nyc.anova.raw2
+
+#Attaching the data set
+attach(nyc.anova)
+#Creating a function
+nycsummary<-function(x){
+  result<-c(length(x),mean(x),sd(x),sd(x)/sqrt(length(x)), min(x), max(x), IQR(x))
+  names(result)<-c("N","Mean","SD","SE","Min","Max","IQR")
+  return(result)
+}
+#Creating a summary stats table
+nycsumstats<-aggregate(price~neighbourhood_group*room_type,data=nyc.anova,nycsummary)
+nycsumstats<-cbind(nycsumstats[,1:2],nycsumstats[,-(1:2)])
+nycsumstats
 ```
 
-#### Model selection attempts
+#### Summary Statistics Graph
+#- The below graph shows characteristics of a nonadditive model
+#- Next Steps:
+#  1. Fit a non-additive model
+#  2. Check the assumptions
+#  3. Exmine Type III Sum of Squares F-test tables
 
-```{r intuitive model}
-#To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared
-rfit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
-summary(rfit)
-plot(rfit)
-rfitl <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc4)
-summary(rfitl)
-plot(rfitl)
+```{r sumstats graph}
+ggplot(nycsumstats,aes(x=room_type,y=Mean,group=neighbourhood_group,colour=neighbourhood_group))+
+  ylab("NYC AirBnBs Prices")+xlab("Room Type")+
+  geom_line()+
+  geom_point()+
+  geom_errorbar(aes(ymin=Mean-SD,ymax=Mean+SD),width=.1)
 ```
 
-```{r forward selection model}
-nyc.fwd = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method = "forward", data=log.nyc, nvmax=20)
-summary(nyc.fwd)$adjr2
+#### Nonadditive 2-Way ANOVA
+- QQ Plot for assumption assessment
+  - Show a curve, needs transformation
 
-fwd.adjr2 <- summary(nyc.fwd)$adjr2
-plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
-fwd.index <- which(adjr2 == max(adjr2))
-points(fwd.index, adjr2[fwd.index],col="red", pch=10)
+```{r nonadditive model assumptions check}
+#The following code fits the nonadditive two way anova model and then produces the first the main residual diagnostics for assumption checking
+nyc.model.fit<-aov(price~neighbourhood_group+room_type+neighbourhood_group:room_type,data=nyc.anova)
+
+nyc.fits <- data.frame(fitted.values=nyc.model.fit$fitted.values,residuals=nyc.model.fit$residuals)
+
+#Reisudals vs Fitted
+nyc.plot1 <- ggplot(nyc.fits, aes(x=fitted.values,y=residuals))+ylab("Residuals")+
+  xlab("Predicted")+geom_point()
+#QQ Plot of residuals #Note the diagonal abline is only good for qqplots of normal data
+nyc.plot2 <- ggplot(nyc.fits,aes(sample=residuals))+
+  stat_qq()+geom_abline(intercept=mean(nyc.fits$residuals), slope = sd(nyc.fits$residuals))
+#Histograms of residuals
+nyc.plot3 <- ggplot(nyc.fits, aes(x=residuals)) + 
+  geom_histogram(aes(y=..density..),binwidth=1,color="black", fill="gray")+
+  geom_density(alpha=.1, fill="red")
+#Grid of all 3 graphs above
+grid.arrange(nyc.plot1, nyc.plot2, nyc.plot3, ncol=3)
 ```
 
-- Below are the final coeffecients based on the above forwad selection model with highest Adjusted r-squared at 15
-
-```{r}
-coef(nyc.fwd,15)
+```{r nonadditive assumptions check 2}
+par(mfrow=c(2,2))
+plot(nyc.model.fit)
 ```
 
-```{r backward selection model}
-nyc.bck = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="backward", data=log.nyc, nvmax=20)
-summary(nyc.bck)$adjr2
+#### Log transformation on price
 
-bck.adjr2 <- summary(nyc.bck)$adjr2
-plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
-bck.index <- which(adjr2 == max(adjr2))
-points(bck.index, adjr2[bck.index],col="red", pch=10)
+```{r log transformation on price}
+#Transforming price to logged variable
+nyc.log.anova <- nyc.anova %>% mutate(lprice=log(price))
+#view(nyc.final)
 ```
 
-- Below are the final coeffecients based on the above backward selection model with highest Adjusted r-squared at 15
+#### Assumptions check on log transformation of price
+- Equal variances: there is some slight variation of variances but this will suffice in order to move forward
+- QQ Plot: there is still some slight departure from normality, but again this is acceptable to move forward with our model
+- DON'T FORGET TO MENTION CLT - Central Limit Theorum
 
-```{r}
-coef(nyc.bck,15)
+```{r nonadditive log assumptions check}
+nyc.model.fit.log<-aov(lprice~neighbourhood_group+room_type+neighbourhood_group:room_type,data=nyc.log.anova)
+
+nyc.fits.log <- data.frame(fitted.values=nyc.model.fit.log$fitted.values,residuals=nyc.model.fit.log$residuals)
+
+#Reisudals vs Fitted
+nyc.logplot1 <- ggplot(nyc.fits.log, aes(x=fitted.values,y=residuals))+ylab("Residuals")+
+  xlab("Predicted")+geom_point()
+#QQ Plot of residuals #Note the diagonal abline is only good for qqplots of normal data
+nyc.logplot2 <- ggplot(nyc.fits.log,aes(sample=residuals))+
+  stat_qq()+geom_abline(intercept=mean(nyc.fits.log$residuals), slope = sd(nyc.fits.log$residuals))
+#Histograms of residuals
+nyc.logplot3 <- ggplot(nyc.fits.log, aes(x=residuals)) + 
+  geom_histogram(aes(y=..density..),binwidth=1,color="black", fill="gray")+
+  geom_density(alpha=.1, fill="red")
+#Grid of all 3 graphs above
+grid.arrange(nyc.logplot1, nyc.logplot2, nyc.logplot3, ncol=3)
 ```
 
-```{r seqrep selection model}
-nyc.seq = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="seqrep", data=log.nyc, nvmax=20)
-summary(nyc.seq)$adjr2
-
-bck.adjr2 <- summary(nyc.bck)$adjr2
-plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
-bck.index <- which(adjr2 == max(adjr2))
-points(bck.index, adjr2[bck.index],col="red", pch=10)
+par(mfrow=c(2,2))
+```{r non additive log assumptions check2}
+plot(nyc.model.fit.log)
 ```
 
-```{r exhaustive selection model}
-#Due to an exhaustive method being too large. We are commenting out this model and moving forward with selective methods that will run
-#nyc.exh = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, data=log.nyc, nvmax=20)
-#summary(nyc.exh)$adjr2
-#summary(nyc.exh)$rss
-#summary(nyc.exh)$bic
+#### Outliers
+- Since there are not singular points that are aggressively skewing the data, these outliers aren't considered unique or affecting the model in a way that would not be logical.
+- Choose to leave all low and high end metrics since the model should take these into account
+
+#### Type III F-test table
+- From the below F-test table we can see that neighborhood_group, room_type, as well as their interaction are all statistically significant for this model
+- The type-3 sums of squares F-test is provided below.
+The test for an interaction is not significant (F-stat: 12.493 p-value < .0001).
+Therefore, we can conclude that the potential changes in AirBnB price for one of the factors does depend on the other.
+
+```{r Ftest}
+Anova(nyc.model.fit, type = 3)
 ```
 
-#### Assumptions Check on Intuitive Model
-- Residuals near normally distributed but still skewed
-- Envoking Central Limit Theorum due to such a large sample size
-- Constant Variance
-  - The QQ Plot shows an extreme deviation from normality. Even with the Central Limit Theorum we do not feel comforablte moving forward.
-
-### XXXXXXXX
-
-```{r Assumptions Check on Intuitive Model}
-par(mfrow=c(2,2))
-full.model<-lm(price~.,data=nyc4)
-plot(XXXXXXX)
+```{r log Ftest}
+Anova(nyc.model.fit.log,type=3)
 ```
 
-#### Assumptions Check on Log-Linear Intuitive Model
-- Risduals are near normally distributed with them being slightly off
-  - Envoking Central Limit Theorum due to such a large sample size
-  - Passed
-- Constant variance
-  - The QQ-plot is showing much less departure from normality
-  - Passed
-
-### XXXXXXXXX
-
-```{r Assumptions Check on Log-Linear Intuitive Model}
-par(mfrow=c(2,2))
-log.depend.model<-lm(lprice~.,data=log.nyc)
-plot(log.depend.model)
+```{r ftest CIs}
+#Confidence Intervals for F Test
+confint(nyc.model.fit.log)
 ```
 
-- Independence
-  - Assumed
-  - Passed
-- Multicollinearity
-  - We are seeing a high VIF for our distance to Times Square
+#### Multiple Test Technique on No Transformation: Tukey-Kramer
+- From the F-test table we can see that all current variables are statistically significnat at the 0.05 alpha level
+- Move forward with the Tukey-Kramer to discover what factors and/or combinations contribute to predicting the price of a NYC AirBnB
 
-```{r Multicollinearity Assumption on Log-Linear Intuitive Model}
-vif(log.depend.model)[,3]^2
+```{r adjp tukey}
+nyc.anova.diff <- TukeyHSD(nyc.model.fit,"neighbourhood_group:room_type", conf.level = .95)
+nyc.anova.diff
 ```
 
-#### MLR May Not Be The Best
-- Multiple linear regression is just one option in building a predictive model for a continuous response
-- We are seeing it as a bad option because
-  - The true relationship between the response and predictors is NOT “linear”.  The relationships are complex.
-    - We have gotten close, but we have worked extremely hard in specifying our model and manipulating the raw data to surface a linear relationship
-    - This makes the interpretation into the real world application difficult to interpret
-  - Since the above is true and our data is very large, we think that other methods such as Random Forest or K-NN would perform better.
-    - These options are less time consuming because the model complexity is built into the lagorithm
-    - We also do not have to specify how a relationship exists ahead of time
-- Since we see a strong relationship between the categorical variables, we move forward with a Two-Way ANOVA model to create a model way predict the price of a NYC AirBnB.
+```{r adjup tukey graph}
+plot(TukeyHSD(nyc.model.fit,"neighbourhood_group:room_type", conf.level = .95))
+```
+
+```{r sig pvalues}
+nyc.anova.diff2 = tidy(nyc.anova.diff)
+colnames(nyc.anova.diff2)[3] <- "diff"
+invisible(view(nyc.anova.diff2))
+
+nyc.anova.diffdf <- nyc.anova.diff2[nyc.anova.diff2$adj.p.value <0.05,]
+nyc.anova.diffdf <- nyc.anova.diffdf[order(nyc.anova.diffdf$diff),]
+nyc.anova.diffdf
+```
+
+#### Multiple Test Technique on Log Transformationl: Tukey-Kramer
+- From the F-test table we can see that all current variables are statistically significnat at the 0.05 alpha level
+- Move forward with the Tukey-Kramer to discover what factors and/or combinations contribute to predicting the price of a NYC AirBnB
+
+```{r log tukey pvalues}
+#nyc.anova.log.diff <- TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95)
+#nyc.anova.log.diff
+```
+
+```{r log tukey plot CI}
+#plot(TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95))
+```
+
+#### Back Transformation
+- To keep the data easily interpretable we have moved our nyc.anova.diff results into a data frame and are now going to back transform the diff and upper and lower confidence interval results.
+
+```{r log back transformation}
+#nyc.anova.log.diff2 = tidy(nyc.anova.log.diff)
+#colnames(nyc.anova.log.diff2)[3] <- "diff"
+#invisible(view(nyc.anova.log.diff2))
+
+#nyc.anova.log.diffdf <- nyc.anova.log.diff2[nyc.anova.log.diff2$adj.p.value <0.05,]
+#invisible(yc.anova.log.diffdf)
+
+#ConfInt_Diff_Backlog <- yc.anova.log.diffdf %>% mutate(Tdiff = exp(diff))
+#ConfInt_Diff_Backlog <- ConfInt_Diff_Backlog %>% mutate(Tlow = exp(conf.low))
+#ConfInt_Diff_Backlog <- ConfInt_Diff_Backlog %>% mutate(Thigh = exp(conf.high))
+
+#ConfInt_Diff_Backlog <- select(ConfInt_Diff_Backlog, -c("diff", "conf.low", "conf.high"))
+#ConfInt_Diff_Backlog <- ConfInt_Diff_Backlog[order(-ConfInt_Diff_Backlog$Tdiff),]
+#ConfInt_Diff_Backlog
+```

### 2020-02-11 Codebooks/MSDS6372.Project.O1.Rmd

@@
 plot(rfit)
+
 rfitl <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc4)

### 2020-02-15 WorkingCode/Project1_RM_Objective_1.Rmd
Add files via upload

---
title:  "Project1_RM_Objective_1"
Author: "Reagan Meagher"
Date:   "2/10/2020"
---

----------
  SETUP
----------

```{r setup and clear envirornment, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
rm(list = ls()) #Clear envirornment code
options(scipen=999) #No exponential formatting of numbers
options(max.print=1000000)
```

```{r libraries}
library(tidyverse)
library(caret)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
library(SamplingStrata)
library(rbin)
library(leaps)
library(dplyr)
library(ggplot2)
library(geosphere)
library(broom)
library(plyr)
```

----------
   EDA
----------

```{r EDA, create linear-linear data set}
nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_1/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
nyc <- nycraw

#Creating a new, tsquare_distance (distance to Times Square in miles)
for (i in 1:nrow(nyc)) {
  n <- (distHaversine(c(nyc$latitude[i], -nyc$longitude[i]), c(40.7580, 73.9855)) / 1609.344)
  nyc$tsquare_distance[i] <- n
}

#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighborhood"
nyc <- select(nyc, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood_group"))

#### Zero Value Variable Check
#- Checking on dependent variable range to make sure if there are zero's to remove. It would not be free to stay in NYC.
#- Checking on independent variables that have '0' as a value. Seeing that "availability_365" would mean the AirBnB isn't available at all, we are dropping those from our data set.
nyc <- nyc[!(nyc$price==0),]
nyc <- nyc[!(nyc$availability_365==0),]

#Checking for NAs
#md.pattern(nyc)
#Drop NAs that are present
nyc <- na.omit(nyc)
#Confirming NA drop
#nrow(nyc)

#Storing categorical variables as factors
skim(nyc)

#Removing reviews_per_month due to high correlation of is and number_of_reviews
nyc <- select(nyc, -c("reviews_per_month"))

#Generate a summary of the current data set
#summary(nyc)

#Restricting data set to prices between $25 and $400 a night (affordable market)
nyc <- filter(nyc, price >= 25 & price <= 400)

#Removing outliers of minimum nights stay
nyc <- nyc[!(nyc$minimum_nights > 365),]
#invisible(view(nyc))

#Creating linear-linear data set
linear.nyc <- nyc

#Linearity check of linear-linear data set
#pairs(nyc,col=nyc$neighbourhood) #Color by neighborhood
```

```{r create log-linear data set}
log.nyc <- nyc %>% mutate(lprice=log(price))
log.nyc <- select(log.nyc, -c("price"))
invisible(log.nyc)

#Linearity check of log-linear data set
#pairs(log.nyc,col=log.nyc$neighbourhood)
```

```{r create log-log data set}
log.log.nyc <- log.nyc %>% mutate(lreviews=log(number_of_reviews))
log.log.nyc <- log.log.nyc %>% mutate(lnights=log(minimum_nights))
log.log.nyc <- log.log.nyc %>% mutate(llistings=log(calculated_host_listings_count))
log.log.nyc <- log.log.nyc %>% mutate(lavailablility=log(availability_365))
log.log.nyc <- log.log.nyc %>% mutate(ltsqr=log(tsquare_distance))
invisible(log.log.nyc)

log.log.nyc <- select(log.log.nyc, -c("minimum_nights", "number_of_reviews", "calculated_host_listings_count", "availability_365", "tsquare_distance"))
# Checking for -inf logged results
invisible(log.log.nyc)
# Drop -inf log reults in lavailability
log.log.nyc<-log.log.nyc[!(log.log.nyc$lavailablility=="-Inf"),]
invisible(log.log.nyc)

#Linearity Check of log-log data set
#pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood) #Color by neighborhood
```

```{r create 90/10 train/test splits for each data source}
#Really handy predict function
predict.regsubsets =function (object , newdata ,id ,...){
  form=as.formula (object$call [[2]])
  mat=model.matrix(form ,newdata )
  coefi=coef(object ,id=id)
  xvars=names(coefi)
  mat[,xvars]%*%coefi
}
```

----------
 MODELING
----------

TEST/TRAIN CREATION
```{r create 90/10 train/test splits for each data source}
set.seed(100)

#nyc
index<-sample(1:dim(linear.nyc)[1],nrow(linear.nyc)*.9,replace=F)
linear.train<-linear.nyc[index,]
linear.test<-linear.nyc[-index,]

#log.nyc
index<-sample(1:dim(log.nyc)[1],nrow(log.nyc)*.9,replace=F)
log.train<-log.nyc[index,]
log.test<-log.nyc[-index,]
```

INTUITIVE LINEAR - LINEAR
```{r intuitive model building}
#LINEAR - LINEAR
linear.intuitive.train.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = linear.train)
linear.intuitive.predictions <- linear.intuitive.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.intuitive.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.intuitive.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.intuitive.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.intuitive.predictions, linear.test$price)/mean(linear.test$price)

linear.intuitive.final.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(linear.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.intuitive.final.model)^2))
summary(linear.intuitive.final.model)
par(mfrow=c(2,2))
plot(linear.intuitive.final.model)
confint(linear.intuitive.final.model)
```

INTUITIVE LOG - LINEAR
```{r intuitive model building}
#LOG - LINEAR
log.intuitive.test.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.train)
log.intuitive.predictions <- log.intuitive.test.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.intuitive.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.intuitive.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.intuitive.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.intuitive.predictions, log.test$lprice)/mean(log.test$lprice)

log.intuitive.final.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(log.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(log.intuitive.final.model)^2))
summary(log.intuitive.final.model)
par(mfrow=c(2,2))
plot(log.intuitive.final.model)
confint(log.intuitive.final.model)
```

------------------------------------------------------------------

FORWARD LINEAR
```{r forward selection model}
#FORWARD LINEAR
set.seed(77)

linear.forward.select.model = regsubsets(price~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365,data=linear.train,method="forward",nvmax=500)

par(mfrow=c(1,3))
fwd.bic <- summary(linear.forward.select.model)$bic
plot(1:length(summary(linear.forward.select.model)$bic), fwd.bic, type = "l", ylab = "BIC", xlab = "# Of Predictors")
fwd.index.bic <- which(fwd.bic == min(fwd.bic))
points(fwd.index.bic, fwd.bic[fwd.index.bic],col="red", pch=10)
print("")
print("Selected Number of Predictors From Forward Selection (BIC)")
print(fwd.index.bic)

fwd.adjr2 <- summary(linear.forward.select.model)$adjr2
plot(1:length(summary(linear.forward.select.model)$adjr2), fwd.adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
fwd.index.adjr2 <- which(fwd.adjr2 == max(fwd.adjr2))
points(fwd.index.adjr2, fwd.adjr2[fwd.index.adjr2],col="red", pch=10)
print("")
print("Selected Number of Predictors From Forward Selection (AR2)")
print(fwd.index.adjr2)

fwd.rss <- summary(linear.forward.select.model)$rss
plot(1:length(summary(linear.forward.select.model)$rss), fwd.rss, type = "l", ylab = "RSS", xlab = "# Of Predictors")
fwd.index.rss <- which(fwd.rss == min(fwd.rss))
points(fwd.index.rss, fwd.rss[fwd.index.rss],col="red", pch=10)
print("")
print("Selected Number of Predictors From Forward Selection (RSS)")
print(fwd.index.rss)

linear.forward.select.model2 = regsubsets(price~.,data=linear.train,method="forward",nvmax=(fwd.index.bic)+1)
coef(linear.forward.select.model2,fwd.index.bic)

linear.forward.train.model <-lm(price~neighbourhood + number_of_reviews + minimum_nights + calculated_host_listings_count + room_type + tsquare_distance,data=linear.train)
linear.forward.predictions <- linear.forward.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.forward.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.forward.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.forward.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.forward.predictions, linear.test$price)/mean(linear.test$price)

linear.forward.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.forward.final.model))
print("Full Model BIC: ")
print(BIC(linear.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.forward.final.model)^2))
summary(linear.forward.final.model)
par(mfrow=c(2,2))
plot(linear.forward.final.model)
```

FORWARD LOG
```{r forward selection model}
#FORWARD LOG
set.seed(77)

log.forward.select.model = regsubsets(lprice~.,data=log.train,method="forward",nvmax=500)

par(mfrow=c(1,3))
fwd.bic <- summary(log.forward.select.model)$bic
plot(1:length(summary(log.forward.select.model)$bic), fwd.bic, type = "l", ylab = "BIC", xlab = "# Of Predictors")
fwd.index.bic <- which(fwd.bic == min(fwd.bic))
points(fwd.index.bic, fwd.bic[fwd.index.bic],col="red", pch=10)
print("")
print("Selected Number of Predictors From Forward Selection (BIC)")
print(fwd.index.bic)

fwd.adjr2 <- summary(log.forward.select.model)$adjr2
plot(1:length(summary(log.forward.select.model)$adjr2), fwd.adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
fwd.index.adjr2 <- which(fwd.adjr2 == max(fwd.adjr2))
points(fwd.index.adjr2, fwd.adjr2[fwd.index.adjr2],col="red", pch=10)
print("")
print("Selected Number of Predictors From Forward Selection (AR2)")
print(fwd.index.adjr2)

fwd.rss <- summary(log.forward.select.model)$rss
plot(1:length(summary(log.forward.select.model)$rss), fwd.rss, type = "l", ylab = "RSS", xlab = "# Of Predictors")
fwd.index.rss <- which(fwd.rss == min(fwd.rss))
points(fwd.index.rss, fwd.rss[fwd.index.rss],col="red", pch=10)
print("")
print("Selected Number of Predictors From Forward Selection (RSS)")
print(fwd.index.rss)

log.forward.select.model2 = regsubsets(lprice~.,data=log.train,method="forward",nvmax=(fwd.index.bic)+1)
coef(log.forward.select.model2,fwd.index.bic)

log.forward.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.forward.predictions <- log.forward.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.forward.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.forward.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.forward.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.forward.predictions, log.test$lprice)/mean(log.test$lprice)

log.forward.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.forward.final.model))
print("Full Model BIC: ")
print(BIC(log.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.forward.final.model)^2))
summary(log.forward.final.model)
par(mfrow=c(2,2))
plot(log.forward.final.model)
```

BACKWARD LINEAR
```{r backward selection model}
set.seed(77)

linear.backward.select.model = regsubsets(price~.,data=linear.train,method="backward",nvmax=500)

par(mfrow=c(1,3))
bkwrd.bic <- summary(linear.backward.select.model)$bic
plot(1:length(summary(linear.backward.select.model)$bic), bkwrd.bic, type = "l", ylab = "BIC", xlab = "# Of Predictors")
bkwrd.index.bic <- which(bkwrd.bic == min(bkwrd.bic))
points(bkwrd.index.bic, bkwrd.bic[bkwrd.index.bic],col="red", pch=10)
print("")
print("Selected Number of Predictors From backward Selection (BIC)")
print(bkwrd.index.bic)

bkwrd.adjr2 <- summary(linear.backward.select.model)$adjr2
plot(1:length(summary(linear.backward.select.model)$adjr2), bkwrd.adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
bkwrd.index.adjr2 <- which(bkwrd.adjr2 == max(bkwrd.adjr2))
points(bkwrd.index.adjr2, bkwrd.adjr2[bkwrd.index.adjr2],col="red", pch=10)
print("")
print("Selected Number of Predictors From backward Selection (AR2)")
print(bkwrd.index.adjr2)

bkwrd.rss <- summary(linear.backward.select.model)$rss
plot(1:length(summary(linear.backward.select.model)$rss), bkwrd.rss, type = "l", ylab = "RSS", xlab = "# Of Predictors")
bkwrd.index.rss <- which(bkwrd.rss == min(bkwrd.rss))
points(bkwrd.index.rss, bkwrd.rss[bkwrd.index.rss],col="red", pch=10)
print("")
print("Selected Number of Predictors From backward Selection (RSS)")
print(bkwrd.index.rss)

linear.backward.select.model2 = regsubsets(price~.,data=linear.train,method="backward",nvmax=(bkwrd.index.bic)+1)
coef(linear.backward.select.model2,bkwrd.index.bic)

linear.backward.train.model <-lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
linear.backward.predictions <- linear.backward.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.backward.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.backward.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.backward.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.backward.predictions, linear.test$price)/mean(linear.test$price)

linear.backward.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.backward.final.model))
print("Full Model BIC: ")
print(BIC(linear.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.backward.final.model)^2))
summary(linear.backward.final.model)
par(mfrow=c(2,2))
plot(linear.backward.final.model)
```

BACKWARD LOG
```{r backward selection model}
set.seed(77)

log.backward.select.model = regsubsets(lprice~.,data=log.train,method="backward",nvmax=500)

par(mfrow=c(1,3))
bkwrd.bic <- summary(log.backward.select.model)$bic
plot(1:length(summary(log.backward.select.model)$bic), bkwrd.bic, type = "l", ylab = "BIC", xlab = "# Of Predictors")
bkwrd.index.bic <- which(bkwrd.bic == min(bkwrd.bic))
points(bkwrd.index.bic, bkwrd.bic[bkwrd.index.bic],col="red", pch=10)
print("")
print("Selected Number of Predictors From backward Selection (BIC)")
print(bkwrd.index.bic)

bkwrd.adjr2 <- summary(log.backward.select.model)$adjr2
plot(1:length(summary(log.backward.select.model)$adjr2), bkwrd.adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
bkwrd.index.adjr2 <- which(bkwrd.adjr2 == max(bkwrd.adjr2))
points(bkwrd.index.adjr2, bkwrd.adjr2[bkwrd.index.adjr2],col="red", pch=10)
print("")
print("Selected Number of Predictors From backward Selection (AR2)")
print(bkwrd.index.adjr2)

bkwrd.rss <- summary(log.backward.select.model)$rss
plot(1:length(summary(log.backward.select.model)$rss), bkwrd.rss, type = "l", ylab = "RSS", xlab = "# Of Predictors")
bkwrd.index.rss <- which(bkwrd.rss == min(bkwrd.rss))
points(bkwrd.index.rss, bkwrd.rss[bkwrd.index.rss],col="red", pch=10)
print("")
print("Selected Number of Predictors From backward Selection (RSS)")
print(bkwrd.index.rss)

log.backward.select.model2 = regsubsets(lprice~.,data=log.train,method="backward",nvmax=(bkwrd.index.bic)+1)
coef(log.backward.select.model2,bkwrd.index.bic)

log.backward.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.backward.predictions <- log.backward.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.backward.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.backward.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.backward.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.backward.predictions, log.test$lprice)/mean(log.test$lprice)

log.backward.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.backward.final.model))
print("Full Model BIC: ")
print(BIC(log.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.backward.final.model)^2))
summary(log.backward.final.model)
par(mfrow=c(2,2))
plot(log.backward.final.model)
```

SEQREP LINEAR
```{r seqrep selection model}
set.seed(77)

linear.seqrep.select.model = regsubsets(price~.,data=linear.train,method="seqrep",nvmax=500)

par(mfrow=c(1,3))
srep.bic <- summary(linear.seqrep.select.model)$bic
plot(1:length(summary(linear.seqrep.select.model)$bic), srep.bic, type = "l", ylab = "BIC", xlab = "# Of Predictors")
srep.index.bic <- which(srep.bic == min(srep.bic))
points(srep.index.bic, srep.bic[srep.index.bic],col="red", pch=10)
print("")
print("Selected Number of Predictors From seqrep Selection (BIC)")
print(srep.index.bic)

srep.adjr2 <- summary(linear.seqrep.select.model)$adjr2
plot(1:length(summary(linear.seqrep.select.model)$adjr2), srep.adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
srep.index.adjr2 <- which(srep.adjr2 == max(srep.adjr2))
points(srep.index.adjr2, srep.adjr2[srep.index.adjr2],col="red", pch=10)
print("")
print("Selected Number of Predictors From seqrep Selection (AR2)")
print(srep.index.adjr2)

srep.rss <- summary(linear.seqrep.select.model)$rss
plot(1:length(summary(linear.seqrep.select.model)$rss), srep.rss, type = "l", ylab = "RSS", xlab = "# Of Predictors")
srep.index.rss <- which(srep.rss == min(srep.rss))
points(srep.index.rss, srep.rss[srep.index.rss],col="red", pch=10)
print("")
print("Selected Number of Predictors From seqrep Selection (RSS)")
print(srep.index.rss)

linear.seqrep.select.model2 = regsubsets(price~.,data=linear.train,method="seqrep",nvmax=(srep.index.bic)+1)
coef(linear.seqrep.select.model2,srep.index.bic)

linear.seqrep.train.model <-lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
linear.seqrep.predictions <- linear.seqrep.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.seqrep.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.seqrep.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.seqrep.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.seqrep.predictions, linear.test$price)/mean(linear.test$price)

linear.seqrep.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(linear.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.seqrep.final.model)^2))
summary(linear.seqrep.final.model)
par(mfrow=c(2,2))
plot(linear.seqrep.final.model)
```

seqrep LOG
```{r seqrep selection model}
set.seed(77)

log.seqrep.select.model = regsubsets(lprice~.,data=log.train,method="seqrep",nvmax=500)

par(mfrow=c(1,3))
srep.bic <- summary(log.seqrep.select.model)$bic
plot(1:length(summary(log.seqrep.select.model)$bic), srep.bic, type = "l", ylab = "BIC", xlab = "# Of Predictors")
srep.index.bic <- which(srep.bic == min(srep.bic))
points(srep.index.bic, srep.bic[srep.index.bic],col="red", pch=10)
print("")
print("Selected Number of Predictors From seqrep Selection (BIC)")
print(srep.index.bic)

srep.adjr2 <- summary(log.seqrep.select.model)$adjr2
plot(1:length(summary(log.seqrep.select.model)$adjr2), srep.adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
srep.index.adjr2 <- which(srep.adjr2 == max(srep.adjr2))
points(srep.index.adjr2, srep.adjr2[srep.index.adjr2],col="red", pch=10)
print("")
print("Selected Number of Predictors From seqrep Selection (AR2)")
print(srep.index.adjr2)

srep.rss <- summary(log.seqrep.select.model)$rss
plot(1:length(summary(log.seqrep.select.model)$rss), srep.rss, type = "l", ylab = "RSS", xlab = "# Of Predictors")
srep.index.rss <- which(srep.rss == min(srep.rss))
points(srep.index.rss, srep.rss[srep.index.rss],col="red", pch=10)
print("")
print("Selected Number of Predictors From seqrep Selection (RSS)")
print(srep.index.rss)

log.seqrep.select.model2 = regsubsets(lprice~.,data=log.train,method="seqrep",nvmax=(srep.index.bic)+1)
coef(log.seqrep.select.model2,srep.index.bic)

log.seqrep.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.seqrep.predictions <- log.seqrep.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.seqrep.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.seqrep.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.seqrep.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.seqrep.predictions, log.test$lprice)/mean(log.test$lprice)

log.seqrep.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(log.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(log.seqrep.final.model)^2))
summary(log.seqrep.final.model)
par(mfrow=c(2,2))
plot(log.seqrep.final.model)
```

### 2020-02-16 WorkingCode/Project1_RM_LL_Objective_1.Rmd
Ridge LASSO and Elastic Net regressions with plots
Added library(glmnet) to top of Reagan's file.
Added Ridge, LASSO, Elastic Net code to bottom of Reagan's code

--- 2020-02-15 WorkingCode/Project1_RM_Objective_1.Rmd
@@
 title:  "Project1_RM_Objective_1"
-Author: "Reagan Meagher"
-Date:   "2/10/2020"
+Author: "Reagan Meagher and Laura Lazarescou"
+Date:   "2/15/2020"
 ---
@@
 library(plyr)
+library(glmnet)
 ```
@@
 ```
+
+## Ridge, LASSO and Elastic Net Regularization and Regression
+
+```{r}
+
+# library(tidyverse) # all included in top of file library statements
+# library(caret)
+# library(glmnet)
+
+# Using train and test datasets created above
+
+# Format Predictors for glmnet() train  (linear and log(price))
+
+x <- model.matrix(price~., linear.train)[,-1]
+xlog <- model.matrix(lprice~., log.train)[,-1]
+
+# Format responses for glmnet() train (linear and log(price))
+
+y <- linear.train$price
+ylog <- log.train$lprice
+
+```
+
+## Linear-Linear Ridge Regularization, glmnet() alpha=0
+
+```{r Ridge}
+# Performing Ridge regression
+# As we mentioned in the previous sections, lambda values have a large effect on coefficients so now we will compute and choose a suitable one.
+# Then we perform a cross validation with the lambda value corresponding to the lowest prediction error before fitting the data to the model and viewing the coefficients.
+
+cv.r <- cv.glmnet(x, y, alpha = 0) # alpha=0 is Ridge Regularization, choose minimum lambda
+cv.r$lambda.min
+model.ridge <- glmnet(x, y, alpha = 0, lambda = cv.r$lambda.min)
+coef(model.ridge)
+plot(cv.r)
+
+## Test Linear Ridge Model for Accuracy, RMSE and R-squared
+
+x.test.ridge <- model.matrix(price ~., linear.test)[,-1]
+predictions.ridge <- model.ridge %>% predict(x.test.ridge) %>% as.vector()
+data.frame(RMSE.r = RMSE(predictions.ridge, linear.test$price),Rsquare.r = R2(predictions.ridge, linear.test$price))
+
+```
+
+## Log-Linear Ridge Regularization, glmnet() alpha=0
+
+```{r Log-Ridge}
+# Performing Log-Linear Ridge regression
+# As we mentioned in the previous sections, lambda values have a large effect on coefficients so now we will compute and choose a suitable one.
+# Then we perform a cross validation with the lambda value corresponding to the lowest prediction error before fitting the data to the model and viewing the coefficients.
+
+cv.r <- cv.glmnet(xlog, ylog, alpha = 0) # alpha=0 is Ridge Regularization, choose minimum lambda
+cv.r$lambda.min
+model.ridgeL <- glmnet(xlog, ylog, alpha = 0, lambda = cv.r$lambda.min)
+coef(model.ridgeL)
+plot(cv.r)
+
+## Test Log-Linear Ridge Model for Accuracy, RMSE and R-squared
+
+xlog.test.ridge <- model.matrix(lprice ~., log.test)[,-1]
+log.predictions.ridge <- model.ridgeL %>% predict(xlog.test.ridge) %>% as.vector()
+data.frame(RMSE.r = RMSE(log.predictions.ridge, log.test$lprice),Rsquare.r=R2(log.predictions.ridge, log.test$lprice))
+```
+
+## Linear-Linear LASSO Regularization, glmnet() alpha=1
+
+```{r Linear LASSO}
+
+cv.L <- cv.glmnet(x, y, alpha = 1) # alpha=1 is LASSO Regularization, choose minimum lambda
+cv.L$lambda.min
+model.lasso <- glmnet(x, y, alpha = 1, lambda = cv.L$lambda.min)
+coef(model.lasso)
+plot(cv.L)
+
+## Test Linear LASSO Model for Accuracy, RMSE and R-squared
+
+x.test.lasso <- model.matrix(price ~., linear.test)[,-1]
+predictions.lasso <- model.lasso %>% predict(x.test.lasso) %>% as.vector()
+data.frame(RMSE.r = RMSE(predictions.lasso, linear.test$price),Rsquare.r = R2(predictions.lasso, linear.test$price))
+```
+
+## Log-Linear LASSO Regression, glmnet() alpha=1
+
+```{r Log-LASSO}
+# Performing Log-Linear LASSO regression
+
+cv.r <- cv.glmnet(xlog, ylog, alpha = 1) # alpha=1 is LASSO Regularization, choose minimum lambda
+cv.r$lambda.min
+model.lassoL <- glmnet(xlog, ylog, alpha = 1, lambda = cv.r$lambda.min)
+coef(model.lassoL)
+plot(cv.r)
+
+## Test Log-Linear LASSO Model for Accuracy, RMSE and R-squared
+
+xlog.test.lasso <- model.matrix(lprice ~., log.test)[,-1]
+log.predictions.lasso <- model.lassoL %>% predict(xlog.test.lasso) %>% as.vector()
+data.frame(RMSE.r = RMSE(log.predictions.lasso, log.test$lprice),Rsquare.r=R2(log.predictions.lasso, log.test$lprice))
+```
+
+## Linear-Linear Elastic Net Regression, selecting alpha=.5
+
+```{r elastic net}
+
+cv.EN <- cv.glmnet(x, y, alpha = .5) # alpha=.5 is a chosen value between 0 and 1
+cv.EN$lambda.min
+model.elasticnet <- glmnet(x, y, alpha = .5, lambda = cv.EN$lambda.min)
+coef(model.elasticnet)
+plot(cv.EN)
+
+## Test Linear Elastic Net Model for Accuracy, RMSE and R-squared
+
+x.test.elasticnet <- model.matrix(price ~., linear.test)[,-1]
+predictions.elasticnet <- model.elasticnet %>% predict(x.test.elasticnet) %>% as.vector()
+data.frame(RMSE.r = RMSE(predictions.elasticnet, linear.test$price),Rsquare.r = R2(predictions.elasticnet, linear.test$price))
+```
+## Log-Linear Elastic Net Regression, selecting alpha=.5
+
+```{r Log-Elastic Net}
+# Performing Log-Linear Elastic Net regression
+
+cv.r <- cv.glmnet(xlog, ylog, alpha = .5) # alpha=.5 is chosen value for Elastic Net Regularization, choose minimum lambda
+cv.r$lambda.min
+model.ENL <- glmnet(xlog, ylog, alpha = .5, lambda = cv.r$lambda.min)
+coef(model.ENL)
+plot(cv.r)
+
+## Test Log-Linear LASSO Model for Accuracy, RMSE and R-squared
+
+xlog.test.EN <- model.matrix(lprice ~., log.test)[,-1]
+log.predictions.EN <- model.ENL %>% predict(xlog.test.EN) %>% as.vector()
+data.frame(RMSE.r = RMSE(log.predictions.EN, log.test$lprice),Rsquare.r=R2(log.predictions.EN, log.test$lprice))
+```
+
+```

### 2020-02-16 WorkingCode/Project1_RM_Objective_1.Rmd
Add files via upload

@@
 title: "Project1_RM_Objective_1"
-Author: "Reagan Meagher"
-Date:   "2/10/2020"
+Date: 2/10/2020
+Author: Reagan Meagher
 ---
@@
 
-```{r create 90/10 train/test splits for each data source}
+```{r hold predict function}
 #Really handy predict function
@@
 INTUITIVE LINEAR - LINEAR
-```{r intuitive model building}
+```{r intuitive model building - linear}
 #LINEAR - LINEAR
@@
 INTUITIVE LOG - LINEAR
-```{r intuitive model building}
+```{r intuitive model building - log}
 #LOG - LINEAR
@@
 FORWARD LINEAR
-```{r forward selection model}
+```{r forward selection model - linear}
 #FORWARD LINEAR
@@
 FORWARD LOG
-```{r forward selection model}
+```{r forward selection model - log}
 #FORWARD LOG
@@
 BACKWARD LINEAR
-```{r backward selection model}
+```{r backward selection model - linear}
 set.seed(77)
@@
 BACKWARD LOG
-```{r backward selection model}
+```{r backward selection model - log}
 set.seed(77)
@@
 SEQREP LINEAR
-```{r seqrep selection model}
+```{r seqrep selection model - linear}
 set.seed(77)
@@
 seqrep LOG
-```{r seqrep selection model}
+```{r seqrep selection model - log}
 set.seed(77)

### 2020-02-16 WorkingCode/Project1_RM_Objective_1.Rmd
Add files via upload

@@
 #Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighborhood"
-nyc <- select(nyc, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood_group"))
+nyc <- select(nyc, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood"))
 
@@
 #Checking for NAs
-#md.pattern(nyc)
+md.pattern(nyc)
 #Drop NAs that are present
@@
 #Confirming NA drop
-#nrow(nyc)
+nrow(nyc)
 
@@
 #summary(nyc)
+
+nyc <- filter(nyc, neighbourhood_group != "Staten Island")
 
@@
 #Linearity check of linear-linear data set
-#pairs(nyc,col=nyc$neighbourhood) #Color by neighborhood
+#pairs(nyc,col=nyc$neighbourhood_group) #Color by neighborhood
 ```
@@
 #Linearity check of log-linear data set
-#pairs(log.nyc,col=log.nyc$neighbourhood)
+#pairs(log.nyc,col=log.nyc$neighbourhood_group)
 ```
@@
 #Linearity Check of log-log data set
-#pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood) #Color by neighborhood
+#pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood_group) #Color by neighborhood
 ```
@@
 TEST/TRAIN CREATION
-```{r create 90/10 train/test splits for each data source}
-set.seed(100)
+```{r create 70/30 train/test splits for each data source}
+set.seed(1234)
 
 #nyc
-index<-sample(1:dim(linear.nyc)[1],nrow(linear.nyc)*.9,replace=F)
+index<-sample(1:dim(linear.nyc)[1],nrow(linear.nyc)*.7,replace=F)
 linear.train<-linear.nyc[index,]
@@
 #log.nyc
-index<-sample(1:dim(log.nyc)[1],nrow(log.nyc)*.9,replace=F)
+index<-sample(1:dim(log.nyc)[1],nrow(log.nyc)*.7,replace=F)
 log.train<-log.nyc[index,]
@@
 #LINEAR - LINEAR
-linear.intuitive.train.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = linear.train)
+linear.intuitive.train.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = linear.train)
 linear.intuitive.predictions <- linear.intuitive.train.model %>% predict(linear.test)
@@
 
-linear.intuitive.final.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = linear.nyc)
+linear.intuitive.final.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = linear.nyc)
 print("Full Model Adjusted R Squared: ")
@@
 #LOG - LINEAR
-log.intuitive.test.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.train)
+log.intuitive.test.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = log.train)
 log.intuitive.predictions <- log.intuitive.test.model %>% predict(log.test)
@@
 
-log.intuitive.final.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc)
+log.intuitive.final.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = log.nyc)
 print("Full Model Adjusted R Squared: ")
@@
 #FORWARD LINEAR
-set.seed(77)
-
-linear.forward.select.model = regsubsets(price~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365,data=linear.train,method="forward",nvmax=500)
+linear.forward.select.model = regsubsets(price~.,data=linear.train,method="forward",nvmax=20)
 
@@
 
-linear.forward.train.model <-lm(price~neighbourhood + number_of_reviews + minimum_nights + calculated_host_listings_count + room_type + tsquare_distance,data=linear.train)
+linear.forward.train.model <-lm(price~neighbourhood_group + number_of_reviews + minimum_nights + calculated_host_listings_count + room_type + tsquare_distance,data=linear.train)
 linear.forward.predictions <- linear.forward.train.model %>% predict(linear.test)
@@
 
-linear.forward.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
+linear.forward.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
 print("Full Model Adjusted R Squared: ")
@@
 #FORWARD LOG
-set.seed(77)
-
 log.forward.select.model = regsubsets(lprice~.,data=log.train,method="forward",nvmax=500)
@@
 
-log.forward.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
+log.forward.train.model <-lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
 log.forward.predictions <- log.forward.train.model %>% predict(log.test)
@@
 
-log.forward.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
+log.forward.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
 print("Full Model Adjusted R Squared: ")
@@
 ```{r backward selection model - linear}
-set.seed(77)
-
 linear.backward.select.model = regsubsets(price~.,data=linear.train,method="backward",nvmax=500)
@@
 
-linear.backward.train.model <-lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
+linear.backward.train.model <-lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
 linear.backward.predictions <- linear.backward.train.model %>% predict(linear.test)
@@
 
-linear.backward.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
+linear.backward.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
 print("Full Model Adjusted R Squared: ")
@@
 ```{r backward selection model - log}
-set.seed(77)
-
 log.backward.select.model = regsubsets(lprice~.,data=log.train,method="backward",nvmax=500)
@@
 
-log.backward.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
+log.backward.train.model <-lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
 log.backward.predictions <- log.backward.train.model %>% predict(log.test)
@@
 
-log.backward.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
+log.backward.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
 print("Full Model Adjusted R Squared: ")
@@
 ```{r seqrep selection model - linear}
-set.seed(77)
-
 linear.seqrep.select.model = regsubsets(price~.,data=linear.train,method="seqrep",nvmax=500)
@@
 
-linear.seqrep.train.model <-lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
+linear.seqrep.train.model <-lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
 linear.seqrep.predictions <- linear.seqrep.train.model %>% predict(linear.test)
@@
 
-linear.seqrep.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
+linear.seqrep.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
 print("Full Model Adjusted R Squared: ")
@@
 
-log.seqrep.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
+log.seqrep.train.model <-lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
 log.seqrep.predictions <- log.seqrep.train.model %>% predict(log.test)
@@
 
-log.seqrep.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
+log.seqrep.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
 print("Full Model Adjusted R Squared: ")

### 2020-02-16 WorkingCode/Project1_RM_Objective_1.2.16.20.Rmd
Add files via upload

--- 2020-02-16 WorkingCode/Project1_RM_Objective_1.Rmd
@@
 plot(linear.intuitive.final.model)
+vif(linear.intuitive.final.model)
 confint(linear.intuitive.final.model)
@@
 plot(log.intuitive.final.model)
+vif(log.intuitive.final.model)
 confint(log.intuitive.final.model)
@@
 plot(linear.forward.final.model)
+vif(linear.forward.final.model)
+confint(linear.forward.final.model)
 ```
@@
 plot(log.forward.final.model)
+vif(log.forward.final.model)
+confint(log.forward.final.model)
 ```
@@
 plot(linear.backward.final.model)
+vif(linear.backward.final.model)
+confint(linear.backward.final.model)
 ```
@@
 plot(log.backward.final.model)
+vif(log.backward.final.model)
+confint(log.backward.final.model)
 ```
@@
 plot(linear.seqrep.final.model)
+vif(linear.seqrep.final.model)
+confint(linear.seqrep.final.model)
 ```
@@
 plot(log.seqrep.final.model)
+vif(log.seqrep.final.model)
+confint(log.seqrep.final.model)
 ```

### 2020-02-16 WorkingCode/Project1_RM_LL_Objective_1.2.16.20.Rmd
RM and LL code combined
Data set excludes neighbourhood_group=Staten Island

--- 2020-02-16 WorkingCode/Project1_RM_Objective_1.2.16.20.Rmd
@@
 title: "Project1_RM_Objective_1"
-Date: 2/10/2020
-Author: Reagan Meagher
+Date: 2/16/2020
+Author: "Reagan Meagher and Laura Lazarescou"
+Output: "html"
 ---
 
-----------
-  SETUP
-----------
+# ----------
+##  SETUP
+# ----------
 
@@
 library(plyr)
+library(glmnet)
 ```
 
-----------
-   EDA
-----------
+# ----------
+##   EDA
+# ----------
 
@@
 ```
+
+## Begin Ridge, LASSO, Elastic Net Analysis
+
+```{r }
+
+## Ridge, LASSO and Elastic Net Regression and Regularization
+## Source:
+
+# https://hackernoon.com/an-introduction-to-ridge-lasso-and-elastic-net-regression-cca60b4b934f
+
+# library(tidyverse) # all included in top of file library statements
+# library(caret)
+# library(glmnet)
+
+# Using train and test datasets created above
+
+# Format Predictors for glmnet() train  (linear and log(price))
+
+x <- model.matrix(price~., linear.train)[,-1]
+xlog <- model.matrix(lprice~., log.train)[,-1]
+
+# Format responses for glmnet() train (linear and log(price))
+
+y <- linear.train$price
+ylog <- log.train$lprice
+
+```
+
+## Linear-Linear Ridge Regularization, glmnet() alpha=0
+
+```{r Ridge}
+# Performing Ridge regression
+# As we mentioned in the previous sections, lambda values have a large effect on coefficients so now we will compute and choose a suitable one.
+# Then we perform a cross validation with the lambda value corresponding to the lowest prediction error before fitting the data to the model and viewing the coefficients.
+
+cv.r <- cv.glmnet(x, y, alpha = 0) # alpha=0 is Ridge Regularization, choose minimum lambda
+cv.r$lambda.min
+model.ridge <- glmnet(x, y, alpha = 0, lambda = cv.r$lambda.min)
+coef(model.ridge)
+plot(cv.r)
+
+## Test Linear Ridge Model for Accuracy, RMSE and R-squared
+
+x.test.ridge <- model.matrix(price ~., linear.test)[,-1]
+predictions.ridge <- model.ridge %>% predict(x.test.ridge) %>% as.vector()
+data.frame(RMSE.r = RMSE(predictions.ridge, linear.test$price),Rsquare.r = R2(predictions.ridge, linear.test$price))
+```
+
+## Log-Linear Ridge Regularization, glmnet() alpha=0
+
+```{r Log-Ridge}
+# Performing Log-Linear Ridge regression
+
+cv.r <- cv.glmnet(xlog, ylog, alpha = 0) # alpha=0 is Ridge Regularization, choose minimum lambda
+cv.r$lambda.min
+model.ridgeL <- glmnet(xlog, ylog, alpha = 0, lambda = cv.r$lambda.min)
+coef(model.ridgeL)
+plot(cv.r)
+
+## Test Log-Linear Ridge Model for Accuracy, RMSE and R-squared
+
+xlog.test.ridge <- model.matrix(lprice ~., log.test)[,-1]
+log.predictions.ridge <- model.ridgeL %>% predict(xlog.test.ridge) %>% as.vector()
+data.frame(RMSE.r = RMSE(log.predictions.ridge, log.test$lprice),Rsquare.r=R2(log.predictions.ridge, log.test$lprice))
+```
+## Linear-Linear LASSO Regularization, glmnet() alpha=1
+
+```{r Linear LASSO}
+
+cv.L <- cv.glmnet(x, y, alpha = 1) # alpha=1 is LASSO Regularization, choose minimum lambda
+cv.L$lambda.min
+model.lasso <- glmnet(x, y, alpha = 1, lambda = cv.L$lambda.min)
+coef(model.lasso)
+plot(cv.L)
+
+## Test Linear LASSO Model for Accuracy, RMSE and R-squared
+
+x.test.lasso <- model.matrix(price ~., linear.test)[,-1]
+predictions.lasso <- model.lasso %>% predict(x.test.lasso) %>% as.vector()
+data.frame(RMSE.r = RMSE(predictions.lasso, linear.test$price),Rsquare.r = R2(predictions.lasso, linear.test$price))
+```
+
+## Log-Linear LASSO Regression, glmnet() alpha=1
+
+```{r Log-LASSO}
+# Performing Log-Linear LASSO regression
+
+cv.r <- cv.glmnet(xlog, ylog, alpha = 1) # alpha=1 is LASSO Regularization, choose minimum lambda
+cv.r$lambda.min
+model.lassoL <- glmnet(xlog, ylog, alpha = 1, lambda = cv.r$lambda.min)
+coef(model.lassoL)
+plot(cv.r)
+
+## Test Log-Linear LASSO Model for Accuracy, RMSE and R-squared
+
+xlog.test.lasso <- model.matrix(lprice ~., log.test)[,-1]
+log.predictions.lasso <- model.lassoL %>% predict(xlog.test.lasso) %>% as.vector()
+data.frame(RMSE.r = RMSE(log.predictions.lasso, log.test$lprice),Rsquare.r=R2(log.predictions.lasso, log.test$lprice))
+```
+
+## Linear-Linear Elastic Net Regression, selecting alpha=.5
+
+```{r elastic net}
+
+cv.EN <- cv.glmnet(x, y, alpha = .5) # alpha=.5 is a chosen value between 0 and 1
+cv.EN$lambda.min
+model.elasticnet <- glmnet(x, y, alpha = .5, lambda = cv.EN$lambda.min)
+coef(model.elasticnet)
+plot(cv.EN)
+
+## Test Linear Elastic Net Model for Accuracy, RMSE and R-squared
+
+x.test.elasticnet <- model.matrix(price ~., linear.test)[,-1]
+predictions.elasticnet <- model.elasticnet %>% predict(x.test.elasticnet) %>% as.vector()
+data.frame(RMSE.r = RMSE(predictions.elasticnet, linear.test$price),Rsquare.r = R2(predictions.elasticnet, linear.test$price))
+```
+## Log-Linear Elastic Net Regression, selecting alpha=.1
+
+```{r Log-Elastic Net}
+# Performing Log-Linear Elastic Net regression
+
+cv.r <- cv.glmnet(xlog, ylog, alpha = .1) # alpha=.1 is chosen value for Elastic Net Regularization, choose minimum lambda
+cv.r$lambda.min
+model.ENL <- glmnet(xlog, ylog, alpha = .1, lambda = cv.r$lambda.min)
+coef(model.ENL)
+plot(cv.r)
+
+## Test Log-Linear LASSO Model for Accuracy, RMSE and R-squared
+
+xlog.test.EN <- model.matrix(lprice ~., log.test)[,-1]
+log.predictions.EN <- model.ENL %>% predict(xlog.test.EN) %>% as.vector()
+data.frame(RMSE.r = RMSE(log.predictions.EN, log.test$lprice),Rsquare.r=R2(log.predictions.EN, log.test$lprice))
+```

### 2020-02-17 Codebooks/MSDS6372.Project.O2.Rmd
Add files via upload

@@
 ```{r log tukey pvalues}
-#nyc.anova.log.diff <- TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95)
-#nyc.anova.log.diff
+nyc.anova.log.diff <- TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95)
+nyc.anova.log.diff
 ```
@@
 ```{r log tukey plot CI}
-#plot(TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95))
+plot(TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95))
 ```

### 2020-02-18 Codebooks/MSDS6372.Project.O2.Rmd
Add files via upload

@@
 #Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighborhood"
-nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood_group"))
+nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood"))
 head(nyc2)
@@
 #nyc4 %>% pairs() No color model
-pairs(nyc4,col=nyc4$neighbourhood) #Color by neighborhood
+pairs(nyc4,col=nyc4$neighbourhood_group) #Color by neighborhood
 ```
@@
 ```{r linearity check of log-linear model}
-pairs(log.nyc,col=log.nyc$neighbourhood)
+pairs(log.nyc,col=log.nyc$neighbourhood_group)
 ```
@@
 ```{r linearity check of log-log model}
-pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood) #Color by neighborhood
+pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood_group) #Color by neighborhood
 ```
@@
 #nyc.bins  %>% pairs() No color model
-pairs(nyc.bins,col=nyc.bins$neighbourhood) #Color by neighborhood
+pairs(nyc.bins,col=nyc.bins$neighbourhood_group) #Color by neighborhood
 ```
@@
 ```{r}
-plot(nyc4$neighbourhood, nyc4$price, xlab = "Neighbourhood", ylab = "Price", title = "Price v Neighbourhood Correlation Check", col=c(7,32,52,82,107)) 
+plot(nyc4$neighbourhood_group, nyc4$price, xlab = "Neighbourhood Group", ylab = "Price", title = "Price v Neighbourhood Group Correlation Check", col=c(7,32,52,82,107)) 
 ```
 
-- Narrowing down neighborhoods (randomly) to confirm neighbourhood is a significant categorical metrics to keep in MLR
+```{r}
+#Narrowing down neighborhoods (randomly) to confirm neighbourhood is a significant categorical metrics to keep in MLR
+#nycNeighborhood <- ddply(nyc4,.(neighbourhood), function(x) x[sample(nrow(x),1),])
 
-```{r}
-nycNeighborhood <- ddply(nyc4,.(neighbourhood), function(x) x[sample(nrow(x),1),])
-
-plot(nycNeighborhood$neighbourhood, nycNeighborhood$price, xlab = "Neighbourhood", ylab = "Price", title = "Price v Neighbourhood Correlation Check") 
+#plot(nycNeighborhood$neighbourhood_group, nycNeighborhood$price, xlab = "Neighbourhood", ylab = "Price", title = "Price v Neighbourhood Correlation Check") 
 ```
@@
 #### Modeling
-- We are not seeing any linear correlation between the dependent and independent numeric varaibles
+- We are not seeing any linear correlation between the dependent and independent numeric (continuous) varaibles
   - We have tried: linear regression, log-linear regression transformation, log-log regression transformation, binning, and outlier drop.
